### 2017-08-31 Example.tex
initial commit

\documentclass[a4paper,twoside]{article}

\usepackage{epsfig}
%\usepackage{subfigure}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{apalike}
\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.

%\subfigtopskip=0pt
%\subfigcapskip=0pt
%\subfigbottomskip=0pt

\begin{document}

\title{Authors' Instructions  \subtitle{Preparation of Camera-Ready Contributions to SCITEPRESS Proceedings} }

\author{\authorname{First Author Name\sup{1}, Second Author Name\sup{1} and Third Author Name\sup{2}}
\affiliation{\sup{1}Institute of Problem Solving, XYZ University, My Street, MyTown, MyCountry}
\affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
}

\keywords{The paper must have at least one keyword. The text must be set to 9-point font size and without the use of bold or italic font style. For more than one keyword, please use a comma as a separator. Keywords must be titlecased.}

\abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}

\onecolumn \maketitle \normalsize \vfill

\section{\uppercase{Introduction}}
\label{sec:introduction}

\noindent Your paper will be part of the conference proceedings
therefore we ask that authors follow the guidelines explained in
this example in order to achieve the highest quality possible
\cite{Smith98}.

Be advised that papers in a technically unsuitable form will be
returned for retyping. After returned the manuscript must be
appropriately modified.

\section{\uppercase{Manuscript Preparation}}

\noindent We strongly encourage authors to use this document for the
preparation of the camera-ready. Please follow the instructions
closely in order to make the volume look as uniform as possible
\cite{Moore99}.

Please remember that all the papers must be in English and without
orthographic errors.

Do not add any text to the headers (do not set running heads) and
footers, not even page numbers, because text will be added
electronically.

For a best viewing experience the used font must be Times New
Roman, except on special occasions, such as program code
\ref{subsubsec:program_code}.

\subsection{Manuscript Setup}

\noindent The template is composed by a set of 7 files, in the
following 2 groups:\\
\noindent {\bf Group 1.} To format your paper you will need to copy
into your working directory, but NOT edit, the following 4 files:
\begin{verbatim}
  - apalike.bst
  - apalike.sty
  - article.cls
  - scitepress.sty
\end{verbatim}

\noindent {\bf Group 2.} Additionally, you may wish to copy and edit
the following 3 example files:
\begin{verbatim}
  - example.bib
  - example.tex
  - scitepress.eps
\end{verbatim}

\subsection{Page Setup}

The paper size must be set to A4 (210x297 mm). The document
margins must be the following:

\begin{itemize}
    \item Top: 3,3 cm;
    \item Bottom: 4,2 cm;
    \item Left: 2,6 cm;
    \item Right: 2,6 cm.
\end{itemize}

It is advisable to keep all the given values because any text or
material outside the aforementioned margins will not be printed.

\subsection{First Section}

This section must be in one column.

\vfill
\subsubsection{Title and Subtitle}

Use the command \textit{$\backslash$title} and follow the given structure in "example.tex". The title and subtitle must be with initial letters
capitalized (titlecased). If no subtitle is required, please remove the corresponding \textit{$\backslash$subtitle} command. In the title or subtitle, words like "is", "or", "then", etc. should not be capitalized unless they are the first word of the subtitle. No formulas or special characters of any form or language are allowed in the title or subtitle.

\subsubsection{Authors and Affiliations}

Use the command \textit{$\backslash$author} and follow the given structure in "example.tex".

\subsubsection{Keywords}

Use the command \textit{$\backslash$keywords} and follow the given structure in "example.tex". Each paper must have at least one keyword. If more than one is specified, please use a comma as a separator. The sentence must end with a period.

\subsubsection{Abstract}

Use the command \textit{$\backslash$abstract} and follow the given structure in "example.tex".
Each paper must have an abstract up to 200 words. The sentence
must end with a period.

\subsection{Second Section}

Files "example.tex" and "example.bib" show how to create a paper
with a corresponding list of references.

This section must be in two columns.

Each column must be 7,5-centimeter wide with a column spacing
of 0,8-centimeter.

The section text must be set to 10-point.

Section, subsection and sub-subsection first paragraph should not
have the first line indent.

To remove the paragraph indentation (only necessary for the
sections), use the command \textit{$\backslash$noindent} before the
paragraph first word.

If you use other style files (.sty) you MUST include them in the
final manuscript zip file.

\subsubsection{Section Titles}

The heading of a section title should be in all-capitals.

Example: \textit{$\backslash$section\{FIRST TITLE\}}

\vfill
\subsubsection{Subsection Titles}

The heading of a subsection title must be with initial letters
capitalized (titlecased).

Words like "is", "or", "then", etc. should not be capitalized unless
they are the first word of the subsection title.

Example: \textit{$\backslash$subsection\{First Subtitle\}}

\subsubsection{Sub-Subsection Titles}

The heading of a sub subsection title should be with initial letters
capitalized (titlecased).

Words like "is", "or", "then", etc should not be capitalized unless
they are the first word of the sub subsection title.

Example: \textit{$\backslash$subsubsection\{First Subsubtitle\}}

\subsubsection{Tables}

Tables must appear inside the designated margins or they may span
the two columns.

Tables in two columns must be positioned at the top or bottom of the
page within the given margins. To span a table in two columns please add an asterisk (*) to the table \textit{begin} and \textit{end} command.

Example: \textit{$\backslash$begin\{table*\}}

\hspace*{1.5cm}\textit{$\backslash$end\{table*\}}\\

Tables should be centered and should always have a caption
positioned above it. The font size to use is 9-point. No bold or
italic font style should be used.

The final sentence of a caption should end with a period.

\begin{table}[h]
\caption{This caption has one line so it is
centered.}\label{tab:example1} \centering
\begin{tabular}{|c|c|}
  \hline
  Example column 1 & Example column 2 \\
  \hline
  Example text 1 & Example text 2 \\
  \hline
\end{tabular}
\end{table}

\begin{table}[h]
\caption{This caption has more than one line so it has to be
justified.}\label{tab:example2} \centering
\begin{tabular}{|c|c|}
  \hline
  Example column 1 & Example column 2 \\
  \hline
  Example text 1 & Example text 2 \\
  \hline
\end{tabular}
\end{table}

Please note that the word "Table" is spelled out.

\subsubsection{Figures}

Please produce your figures electronically, and integrate them into
your document and zip file.

Check that in line drawings, lines are not interrupted and have a
constant width. Grids and details within the figures must be clearly
readable and may not be written one on top of the other.

Figure resolution should be at least 300 dpi.

Figures must appear inside the designated margins or they may span
the two columns.

Figures in two columns must be positioned at the top or bottom of
the page within the given margins. To span a figure in two columns please add an asterisk (*) to the figure \textit{begin} and \textit{end} command.

Example: \textit{$\backslash$begin\{figure*\}}

\hspace*{1.5cm}\textit{$\backslash$end\{figure*\}}

Figures should be centered and should always have a caption
positioned under it. The font size to use is 9-point. No bold or
italic font style should be used.

\begin{figure}[!h]
  %\vspace{-0.2cm}
  \centering
   {\epsfig{file = SCITEPRESS.eps, width = 5.5cm}}
  \caption{This caption has one line so it is centered.}
  \label{fig:example1}
 \end{figure}

\begin{figure}[!h]
  \vspace{-0.2cm}
  \centering
   {\epsfig{file = SCITEPRESS.eps, width = 5.5cm}}
  \caption{This caption has more than one line so it has to be justified.}
  \label{fig:example2}
  \vspace{-0.1cm}
\end{figure}

The final sentence of a caption should end with a period.

Please note that the word "Figure" is spelled out.

\subsubsection{Equations}

Equations should be placed on a separate line, numbered and
centered.\\The numbers accorded to equations should appear in
consecutive order inside each section or within the contribution,
with the number enclosed in brackets and justified to the right,
starting with the number 1.

Example:

\begin{equation}\label{eq1}
    a=b+c
\end{equation}

\subsubsection{Program Code}\label{subsubsec:program_code}

Program listing or program commands in text should be set in
typewriter form such as Courier New.

Example of a Computer Program in Pascal:

\begin{small}
\begin{verbatim}
 Begin
     Writeln('Hello World!!');
 End.
\end{verbatim}
\end{small}

The text must be aligned to the left and in 9-point type.

\vfill
\subsubsection{Reference Text and Citations}

References and citations should follow the Harvard (Author, date)
System Convention (see the References section in the compiled
manuscript). As example you may consider the citation
\cite{Smith98}. Besides that, all references should be cited in the
text. No numbers with or without brackets should be used to list the
references.

References should be set to 9-point. Citations should be 10-point
font size.

You may check the structure of "example.bib" before constructing the
references.

For more instructions about the references and citations usage
please see the appropriate link at the conference website.

\section{\uppercase{Copyright Form}}

\noindent For the mutual benefit and protection of Authors and
Publishers, it is necessary that Authors provide formal written
Consent to Publish and Transfer of Copyright before publication of
the Book. The signed Consent ensures that the publisher has the
Author's authorization to publish the Contribution.

The copyright form is located on the authors' reserved area.

The form should be completed and signed by one author on
behalf of all the other authors.

\section{\uppercase{Conclusions}}
\label{sec:conclusion}

\noindent Please note that ONLY the files required to compile your paper should be submitted. Previous versions or examples MUST be removed from the compilation directory before submission.

We hope you find the information in this template useful in the preparation of your submission.

\section*{\uppercase{Acknowledgements}}

\noindent If any, should be placed before the references section
without numbering. To do so please use the following command:
\textit{$\backslash$section*\{ACKNOWLEDGEMENTS\}}

\vfill
\bibliographystyle{apalike}
{\small
\bibliography{example}}

\section*{\uppercase{Appendix}}

\noindent If any, the appendix should appear directly after the
references without numbering, and not on a new page. To do so please use the following command:
\textit{$\backslash$section*\{APPENDIX\}}

\vfill
\end{document}

### 2017-08-31 paper-review.tex
initial commit

\documentclass[a4paper,twoside]{article}

\usepackage{epsfig}
%\usepackage{subfigure}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{acronym}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{bigstrut}
\usepackage{rotating}
\usepackage{pslatex}
\usepackage{apalike}
\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.

%\subfigtopskip=0pt
%\subfigcapskip=0pt
%\subfigbottomskip=0pt

\newlength{\frameSize}

% --| My Environments |---------------------------------------------------
\newcommand{\vertboxl}[1]{\rotatebox{90}{\parbox{21mm}{\centering #1}}}
\newcommand{\vertboxm}[1]{\rotatebox{90}{\parbox{17mm}{\centering #1}}}
\newcommand{\vertboxs}[1]{\rotatebox{90}{\parbox{14mm}{\centering #1}}}
\newcommand{\vertboxt}[1]{\rotatebox{90}{\parbox{10mm}{\centering #1}}}
\newcommand{\vertboxxt}[1]{\rotatebox{90}{\parbox{7mm}{\centering #1}}}
\newcommand{\sizebox}[2]{\parbox{#1}{\centering #2}}

% --| My Acronyms |---------------------------------------------------
\newacro{CNN}{Convolutional Neural Network}
\newacro{CRF}{Conditional Random Field}
\newacro{FCN}{Fully Convolutional Neural Network}
\newacro{FROC}{Free-Response Receiver Operating Characteristic}
\newacro{GMM}{Gaussian Mixture Model}
\newacro{HOG}{Histogram of Oriented Gradients}
\newacro{PCA}{Principle Component Analysis}

% --| My Macros |-------------------------------------------------------
\newcommand{\upto}{\, ,...\, ,\,}	% ,...,
\newcommand{\fuerdiegilt}{\;|\;}
\newcommand{\etal}{et\,al.}
\newcommand{\xie}{i.e.}
\newcommand{\xeg}{e.g.}
\newcommand{\newR}{\ensuremath{\mathbb{R}}}
\newcommand{\cross}{$\,\times\,$}
\newcommand{\tightcross}{$\times$}
\newcommand{\tighttimes}{{\mkern-1mu\times\mkern-1mu}}
\newcommand{\ve}[1]{\boldsymbol{#1}}
\newcommand{\veb}[1]{\boldsymbol{\overline{#1}}}
\newcommand{\veh}[1]{\boldsymbol{\widehat{#1}}}
\newcommand{\vet}[1]{\widetilde{\boldsymbol{#1}}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\landau}[1]{$\mathcal{O}\left(#1\right)$}
\newcommand{\sign}[1]{\mathrm{sign}(#1)}

% --| Actual variables |-----------------------------------------------
\newcommand{\mne}{\mathit{MNE}}
\newcommand{\map}{\mathit{map}}
\newcommand{\acc}{\mathit{acc}}
\newcommand{\std}{$\mathit{std}$}
\newcommand{\TP}{\mathit{TP}}
\newcommand{\TN}{\mathit{TN}}
\newcommand{\FP}{\mathit{FP}}
\newcommand{\FN}{\mathit{FN}}
\newcommand{\TPR}{\mathit{TPR}}
\newcommand{\TNR}{\mathit{TNR}}
\newcommand{\FPR}{\mathit{FPR}}
\newcommand{\FNR}{\mathit{FNR}}

\begin{document}

\title{Open Set Logo Detection and Retrieval}

\author{\authorname{Andras T\"uzk\"o\sup{1}, Christian Herrmann\sup{1,2}, Daniel Manger\sup{1}, Dieter Willersinn\sup{1}, J\"urgen Beyerer\sup{1,2}}
\affiliation{\sup{1} Fraunhofer IOSB, Karlsruhe, Germany}
\affiliation{\sup{2} Karlsruhe Institute of Technology KIT, Vision and Fusion Lab, Karlsruhe, Germany}
\email{$\lbrace$andras.tuezkoe$|$christian.herrmann$|$daniel.manger$|$dieter.willersinn$\rbrace$@iosb.fraunhofer.de}
%\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
}

\keywords{Logo Detection, Logo Retrieval, Logo Dataset, Trademark Retrieval, Open Set Retrieval, Deep Learning.}

\abstract{
%%TODO write text here, 70-200 words
%motivation:	open set logo retrieval for broadcast analysis, \xeg to judge advertisement effectiveness 
%problem: search for unknown logo classes; find all occurrences of a query logo; challenges: geometric distortions, different types
%approach: two stage concept with detection and comparison, both using a \ac{CNN}, similar to the concept used in other retrieval tasks
%results: general purpose logo detection yields viable results
%conclusion: 
%%
Searching for logos in image data allows several applications, with judging the effectiveness of advertisement in sports event broadcasts being one example. Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a database of images or videos. Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption. To address this issue, an open set logo retrieval method is proposed in this work which can search for previously unfamiliar logos only by one query sample. A two stage concept with an open set logo detection and comparison is proposed similar to other retrieval tasks. Both modules are based on task specific \acp{CNN}. To train the detector with appropriate in-the-wild data, an according novel Logos in the Wild dataset is collected and made publicly available. The proposed method extends the application field in comparison to closed set approaches and improvements over baseline methods derived from these state-of-the-art closed set approaches are shown. 
}

\onecolumn \maketitle \normalsize \vfill

\section{\uppercase{Introduction}}
\label{sec:introduction}
%\noindent- sport event broadcasts \\
%- \ac{CNN}-based \\
%- separation of workflow into detection and comparison stage, similar to person/face re-id/retrieval \\
%- given as query: search image, not a logo class id or logo name \\
%- extension of the all-in-one architecture known from closed set logo retrieval \\
%
%- there exists a wide variety of different kinds of logos as large-scale datasets, such as METU with more than ?? different logo classes, indicate \\
%
%- task: find all occurrences of a query logo including typical variations, such as color inversions
%
%contributions: \\
%  - detection of any logo, not only predefined ones from training data \\
%  - open set logo retrieval system with search image as query \\
%  - introduction of novel logo dataset \\
\noindent Automated search for logos is a desirable task in visual image analysis.
A key application is the effectiveness measurement of advertisements. Being able to find all logos that match a query, for example, a logo of a specific company, in images allows to assess the visual frequency and prominence of logos in TV broadcasts. Typically, these broadcasts are sports events where sponsorship and advertisement is very common. 
This requires a flexible system where the query can easily be defined and switched according to the current task. Especially, also previously unseen logos should be found if one query sample is available.
%In general, open set retrieval is understood as finding instances of the same class in a database given a single instance from this class which has never been seen before. Usually classes originate from the same category with logos being an example. Thus, prior knowledge about this category can be used to build appropriate retrieval methods. In most applications this prior knowledge is given in shape of training data.
This requirement excludes basically all current logo retrieval approaches because they make a closed-world assumption where all searched logos are known beforehand. Instead, this paper focuses on open set logo retrieval where only one sample image of a logo is available.

Consequently, a novel processing strategy for logo retrieval based on a logo detector and a feature extractor is proposed as illustrated in figure~\ref{fig:pipeline}. Similar strategies are known from other open set retrieval tasks, such as face or person retrieval~\cite{bauml2010,herrmann2015b}. Both, the detector and the extractor are task specific \acp{CNN}. For detection, the Faster R-CNN framework~\cite{ren2015} is employed and the extractor is derived from classification networks for the ImageNet challenge~\cite{deng2009}.
%
\begin{figure}[!h]
  %\vspace{-0.2cm}
  \centering
  \includegraphics[width=\linewidth]{img/outline.png}
  \caption{Proposed logo retrieval strategy.}
  \label{fig:pipeline}
\end{figure}

The necessity for open set logo retrieval becomes obvious when having a look at the diversity and amount of existing logos and brands\footnote{The term brand is used in this work as synonym for a single logo class. Thus, a brand might also refer to a product or company name if an according logo exists.}. The METU trademark dataset~\cite{tursun2017} contains, for example, over half a million different logos. Given this number, a closed set approach where all different logos are pretrained within the retrieval system is clearly inappropriate.
This is why our proposed feature extractor generates a discriminative logo descriptor, which generalizes to unseen logos, instead of a mere classification between previously known brands. The well-known high discriminative capabilities of \acp{CNN} allow to construct such a feature extractor.

One challenge for training a general purpose logo detector lies in appropriate training data. Many logo or trademark dataset~\cite{eakins1998,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application. The need for annotated logo bounding boxes in the images limits the number of suitable datasets. Existing logo datasets~\cite{joly2009,kalantidis2011,romberg2011,letessier2012,bianco2015,su2016,bianco2017} with available bounding boxes are often restricted to a very small number of brands and mostly high quality images. Especially, occlusions, blur and variations within a logo type are only partially covered.
To address these shortcomings, a novel in-the-wild logo dataset is collected and made publicly available~\footnote{\url{url//:to.come}}.

The contributions of this work are threefold:
\begin{itemize}
\item A novel open set logo detector which can detect previously unseen logos.
\item An open set logo retrieval system which needs only a single logo image as query.
\item The introduction of a novel in-the-wild logo dataset.
\end{itemize}

%contributions: \\
%  - detection of any logo, not only predefined ones from training data \\
%  - open set logo retrieval system with search image as query \\
%  - introduction of novel logo dataset \\

\section{\uppercase{Related Work}}
\noindent- Logo Retrieval (\xie closed set approaches) \\
Current logo retrieval strategies are generally solving a closed set detection and classification problem. Eggert et.al. \cite{eggert2015} utilized convolutional neural network to extract features from logos and classified them with a set of SVMs to the target classes. Fast R-CNN \cite{girshick2015} was used for the first time to retrieve logos from images by Iandola et al. \cite{iandola2015} and achieved superior results on the FlickrLogos-32 dataset \cite{romberg2011}. Furthermore, R-CNN, Fast R-CNN and Faster R-CNN were used in \cite{bao2016}, \cite{oliveira2016}, \cite{qi2017}. All these works use the same classes for training as for validation.

%- Other retrieval applications (\xeg face, person)
Retrieval scenarios in other domains are basically always considered open set, \xie samples from the currently searched class have never been seen before.
%, because the searched classes are rarely known beforehand. 
This is the case for general purpose image retrieval~\cite{sivic2003}, tattoo retrieval~\cite{manger2012} or for person retrieval in image or video data where face or appearance-based methods are common~\cite{bauml2010,weber2011,herrmann2015b}. The reason is that these in-the-wild scenarios offer usually a too large and impossible to capture variety of object classes. In case of persons, a class would be an identity. Consequently, methods have to be designed and trained on a limited set of classes and have to generalize to previously unseen classes. We argue that this approach is also required for logo retrieval because of the vast amount of existing brands and according logos which cannot be captured in advance.

% Detector Frameworks: Faster R-CNN~\cite{ren2015}, SSD~\cite{liu2016b}, Yolo~\cite{redmon2016}, ...
Earlier systems utilized hand-crafted features to detect objects on images and recognize them. Lowe et al., used Scale and Translation Invariant Features (SIFT) ~\cite{lowe2004} around keypoints, detected with e.g. Harris corner detector ~\cite{harris1988}. Viola and Jones utilized ~\cite{viola2004} Haar-like features and a cascade of weak classifiers (Adaptive Boosting ~\cite{schapire1999}) to detect faces extremely fast. Nowadays, deep learning methods surpass the traditional methods by a wide margin. OverFeat framework ~\cite{sermanet2013} uses sliding windows on multiple scales of the image, and combines the features to detect objects and to classify them. You Only Look Once (YOLO) ~\cite{redmon2015} introduces an end-to-end network for object detection and classification by using bounding box regressors for the first time for localization. It splits the input image into a square grid, where every cell predicts several bounding boxes with probability scores and classification labels. The Single Shot MultiBox Detector (SSD) \cite{liu2015} utilizes convolutional features from multiple layers and concatenates them to detect objects in real time. Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a region proposal network (RPN) to detect objects on feature maps and classifies the found regions by a fully connected network. Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b} is the improvement of Faster R-CNN in terms of inference time by having a network end-to-end fully convolutional. Mask R-CNN \cite{he2017} extends the functionality of Faster R-CNN by extending the network with a classification mask, which allows end-to-end object detection and semantic segmentation with a little overhead.

% Classification Networks: AlexNet, VGG, ResNet, DenseNet
AlexNet \cite{krizhevsky2012b} was the first neural network after the conquest of support vector machines, achieving impressive performance, and won the ImageNet challenge \cite{deng2009} in 2012. It consists of five convolutional layers, each followed by a max-pooling, which counted for a very deep network at that time. VGG \cite{simonyan2014} follows the general architecture of AlexNet with an increased number of convolutional layers achieving better performance. Residual Networks (ResNet) \cite{he2015} utilizes very deep network architecture of 50-151 layers, and adopts skip connections, which is a direct connection from the output of a lower layer (the one lying closer to the input image). These connections address the problem of degradation, which arises when very deep networks are involved, causing performance dropping. DenseNet \cite{huang2016} has also a ResNet-like architecture, and introduces "dense units". The output of these units is connected with every subsequent dense unit's input with concatenation. This results in a much denser network than a conventional feed-forward network.

\section{\uppercase{Logo Detection}}
\noindent- class agnostic detector \\
- different base networks: VGG-CNN-M, VGG16
% TODO
For scene retrieval it is conventional, that one feature is created for an input image. This is achieved either by inferring from the complete image or by searching for key regions and then extracting features from the found regions, which are finally fused into a global feature. For logo retrieval the goal is not the extraction of a global feature, because it would not be descriptive enough to retrieve small objects. Additionally, a global feature usually does not preserve information of the location and the size of the objects, which are also important factors for logo retrieval.

Therefore, first the objects should be detected in the input image. There are a lot of possibilities to search for objects as explained in cha. Girshick et al. \cite{ren2015} proposed the Faster R-CNN, for end to end learning to detect and classify objects on an image. This network has a bounding box regressor for each trained class, thus it is capable to produce object type specific region proposals.

\section{\uppercase{Logo Comparison}}
%TODO write text here

\section{\uppercase{Logo Dataset}}
%\noindent- freely collected from web \\
%- name suggestions: 'Logos in the Wild', 'IOSB Logos' \\
%- how was the dataset collected? \\
%- database statistics \\
%- what is different compared with other datasets? \\
%- what are the benefits? \\
%%TODO Christian
\noindent To train the proposed logo detector, a novel logo dataset is collected to supplement publicly available logo datasets. A comparison to other datasets is given in table~\ref{tab:logoDatasets}.
%
\begin{table*}[t]
\centering
\caption{Publicly available logo datasets in comparison with the novel dataset.}
\label{tab:logoDatasets}
\begin{small}
\begin{tabular}{cl|ccc}
& \multicolumn{1}{c|}{\textbf{dataset}} & \textbf{brands} & \textbf{logo images} & \textbf{RoIs} \bigstrut[b]\\
\hline
\multirow{8}{*}{\vertboxs{public}} & BelgaLogos \cite{joly2009,letessier2012} & 37 & 1,321 & 2,697 \bigstrut[t] \\
& FlickrBelgaLogos \cite{letessier2012} & 37 & 2,697 & 2,697 \\
& Flickr Logos 27 \cite{kalantidis2011} & 27 & 810 & 1,261 \\
& FlickrLogos-32 \cite{romberg2011} & 32 & 2,240 & 3,404 \\
& Logos-32plus \cite{bianco2015,bianco2017} & 32 & 7,830 & 12,300 \\
& TopLogo10 \cite{su2016} & 10 & 700 & 863 \bigstrut[b] \\
\cline{2-5}
& total & 80 (union) & 15,598 & 23,222 \bigstrut \\
\hline
\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 631 & 6,084 & 17,738 \bigstrut[t]
\end{tabular}
\end{small}
\end{table*}
%
The goal is an in-the-wild logo dataset with pictures including logos instead of the pure original logo graphics. In addition, images where the logo does not represent the central dominant part of the image are preferred. See figure~\ref{fig:logoSamples} for a few examples of the collected data.
%
\setlength{\frameSize}{3.7cm}
\begin{figure*}%
\centering%
\includegraphics[height=\frameSize]{img/sample2.png}
\hfill
\includegraphics[height=\frameSize]{img/sample12.png}
\hfill
\includegraphics[height=\frameSize]{img/sample3.png}%
\\
\vspace{1.5mm}%
\includegraphics[height=\frameSize]{img/sample15.png}
\hfill
\includegraphics[height=\frameSize]{img/sample5.png}
\hfill
\includegraphics[height=\frameSize]{img/sample9.png}
\caption{Examples from the collected Logos in the Wild dataset.}%
\label{fig:logoSamples}
\end{figure*}%
%
Following the general suggestions from \cite{bansal2017}, we target for a dataset containing significantly more brands instead of collecting additional image samples for the already covered brands. This is the exact opposite strategy than performed by the Logos-32plus dataset.
Starting with a list of well-known brands and companies, an image web search is performed. Because most other web collected logo datasets mainly rely on Flickr, we choose to use Google image search to broaden the domain. Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `bmw advertisement', `bmw building', `bmw poster' or `bmw store'.

For each search result, the first $N$ images are downloaded, where $N$ is determined by a quick manual inspection to avoid collecting too much garbage. 
%All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
After removing duplicates, this results in 4~to 608~images per searched brand. These images are then one-by-one annotated with bounding boxes or sorted out if unsuitable.
Images are considered unsuitable if they contain no logos or fail the in-the-wild requirement, which is the case for the original raw logo graphics. Taken pictures of such logos and advertisement posters on the other hand are desired to be in the dataset. 
Annotations distinguish between textual and graphical logos as well as different logos from one company as exemplary indicated in figure~\ref{fig:annotatedSample}.
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
\caption{Annotations differentiate between textual and graphical logos.}%
\label{fig:annotatedSample}
\end{figure}%
%
Altogether, the current version of the dataset, which is used in this paper, contains 631 brands with 17,738 annotated bounding boxes. 150 brands occur at least 10 times. An image may contain more than one logo with the maximum being 100 logos in one image. The complete distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 11cm 0cm 0cm, clip]{img/brandDistribution.pdf}%
\caption{Distribution of number of RoIs per brand.}%
\label{fig:brandDistribution}
\end{figure}%
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 11cm 0cm 0cm, clip]{img/logoDistribution.pdf}%
\caption{Distribution of number of RoIs per image.}%
\label{fig:logoDistribution}
\end{figure}%

The collected Logos in the Wild dataset exceeds the size of all related logo datasets as shown in table~\ref{tab:logoDatasets}. Even the union of all related logo datasets contains significantly less brands and RoIs which makes Logos in the Wild a valuable large-scale dataset.
 %Table~\ref{tab:datasetStatistics} gives more details.
The annotation is still an ongoing process and further larger versions of the dataset are expected to be published in the future (??).
%
%Potential uses: 
%In this work, the dataset is mainly used for training purposes
%In addition to the simple use as training data,

\section{\uppercase{Experiments}}
\noindent- explain FROC curve \\
- maybe introduce mAP \\
- explain baseline method(s) \\
concepts/desired experiments \\
- train on public non-Flickr brands \\
- additionally train on own logo dataset \\
- test on FlickrLogos32 test datasets \\

- additional evaluation on own SportsLogos dataset and qualitative results \\

The proposed method is evaluated on the test set of the public FlickrLogos32 dataset including the distractors. Additional experiments are performed on an internal dataset of sports event TV broadcasts. For a proper separation of train and test data, all brands which are present in the FlickrLogos32 test set are removed from the training data. The training set consists of two parts. The union of all public logo datasets and the novel Logos in the Wild dataset. The respective training and test set sizes are listed in table~\ref{tab:trainData}.
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{6pt}
\caption{Train and test set statistics.}
\label{tab:trainTestStatistics}
\begin{small}
\begin{tabular}{l|c}
?? & ?? %TODO
\end{tabular}
\end{small}
\endgroup
\end{table}

In the first step, the detector stage alone is assessed. Then, the combination of detection and comparison for logo retrieval is evaluated. 
Detection and matching performance is measured by the \ac{FROC} curve~\cite{miller1969} which denotes the detection or detection and identification rate versus the number of false detections.

In all cases the \acp{CNN} are trained until convergence which requires ?? to ??k iterations with a batch-size of ??. Training duration depends on the architecture as well as the amount of training data.
%TODO write text here

\subsection{Detection}
%- train 3 different detectors: multi-class Faster R-CNN (maybe RPN), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
%- test on FlickrLogos32 => FROC plot\\
%- test first two detectors on own logo dataset => FROC plot\\
%- Example Detections\\
%%TODO write text here
As baseline, the state-of-the-art closed set logo retrieval method from~\cite{??} is employed and trained on the public portion of the training data.
It is adapted to open set detection by using the RPN scores as detections. This skips the closed set classification part of the network which is pre-trained on different logos than should be detected on the test set.
%Because of the closed set training strategy, only brands occurring in the training set are the final outcome of this detector. 
%Adaptation to open set detection of previously unseen logos is achieved by using the RPN scores before classification as detections.
%Because of the strict separation of train and test brands, and the closed set training strategy
%the RPN scores serve as detections.
The proposed logo detector is first trained on the same public data for comparison. The results in figure~\ref{fig:detectionFroc} indicate that this strategy is superior by a significant margin. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
\caption{FROC curve for FlickrLogos32 test set.}%
\label{fig:brandDistribution}
\end{figure}%
%

Further improvement is achieved by combining the public training data with the novel data.
Adding the Logos in the Wild dataset as additional training data improves the detection results with its large variety of additional training brands. 
This confirms findings from other domains, such as face analysis, where wider training datasets are preferred over deeper ones~\cite{bansal2017}. This means it is better to train on additional different brands than on additional samples per brand.
As direction for future dataset collection, this suggests to focus on additional brands.

\subsection{Retrieval}
- train 4 to 6 additional networks: feature extraction network for public and public+own training data --- use VGG16, ResNet50, DenseNet as base network (either for both training sets or only for the public+own)
- results on FlickrLogos32 => FROC plot\\
- results on own sports data => FROC plot\\
%TODO write text here

In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events. In total, 1,218 annotated frames with more than 10,000 logos from four different events are available in our SportLogo dataset where 3 events are used for training and one as test set. Refer to table~\ref{tab:sportDataStatistics} for details. In comparison to public logo datasets, the logos are usually significantly smaller in these cases and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}.
%
\begin{figure*}%
\centering%
\includegraphics[width=\linewidth]{img/football-1908719_1920_cut.jpg}%
\caption{Example football frame with small logos in the perimeter advertising.}%
\label{fig:footballSample}
\end{figure*}%
%

%Due to copyright reasons this internal dataset cannot be made publicly available.
%
\begin{table}[t]
\centering
\begingroup	
\setlength{\tabcolsep}{5pt}
\caption{SportLogo dataset statistics.}
\label{tab:sportDataStatistics}
\begin{small}
\begin{tabular}{l|cccc}
 & \textbf{phase} & \textbf{brands} & \sizebox{1.0cm}{\textbf{logo images}} & \textbf{RoIs} \bigstrut[b]\\
\hline
football-1 & \multirow{3}{*}{train} & {104} & {331} & {3,329} \bigstrut[t]\\
{ski} & & {27} & {179} & {701} \\
{ice hockey} & & {19} & {410} & {3,920} \bigstrut[b]\\
\hline
{football-2} & test & 40 & 298 & 2,348 \bigstrut\\
%\hline
%{total} & & {143 (union)} & {1,218} & {10,298} \bigstrut[t]\\
\end{tabular}
\end{small}
\endgroup
\end{table}

\section{\uppercase{Conclusions}}
\label{sec:conclusion}
\noindent- significant improvement over baseline
- enables novel applications
- novel large scale in-the-wild logo dataset
%TODO write text here

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vfill
\bibliographystyle{apalike}
{\small
\bibliography{Biblio}}

\vfill
\end{document}

\\

### 2017-09-01 paper-review.tex
Added classification plot.

@@
 \item An open set logo retrieval system which needs only a single logo image as query.
-\item The introduction of a novel in-the-wild logo dataset.
+\item The introduction of a novel large-scale in-the-wild logo dataset.
 \end{itemize}
@@
 \includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
-\caption{FROC curve for FlickrLogos32 test set.}%
-\label{fig:brandDistribution}
+\caption{Detection FROC curve for FlickrLogos32 test set.}%
+\label{fig:detectionFroc}
 \end{figure}%
@@
 \subsection{Retrieval}
-- train 4 to 6 additional networks: feature extraction network for public and public+own training data --- use VGG16, ResNet50, DenseNet as base network (either for both training sets or only for the public+own)
-- results on FlickrLogos32 => FROC plot\\
-- results on own sports data => FROC plot\\
-%TODO write text here
+%- train 4 to 6 additional networks: feature extraction network for public and public+own training data --- use VGG16, ResNet50, DenseNet as base network (either for both training sets or only for the public+own)
+%- describe repeated query logo strategy => 10 sample => mean + std
+%- results on FlickrLogos32 => FROC plot\\
+%- results on own sports data => FROC plot\\
+%%TODO write text here
+%
+For the retrieval experiments, the state-of-the-art closed set logo retrieval method from the previous section is again used as baseline.
+The class probabilities are interpreted as feature vector which is then used to match previously unseen logos.
+For the proposed open set strategy, the best logo detection network from the previous section is used in all cases.
+Detected logos are described by the classification network's output feature.
+Descriptor matching is performed in all cases with cosine similarity.
+Three different state-of-the-art classification architectures, namely VGG16~\cite{simonyan2014}, ResNet101~\cite{he2015} and DenseNet??~\cite{huang2016}, serve as base for the logo classification stage.
+All networks are pretrained on ImageNet and afterwards fine-tuned either on the public logo train set or the combination of the public and the Logos in the Wild train data.
+
+In 10 iterations, each of the 10 FlickrLogos32 train samples for each brand serves as query sample.
+This allows to assess the statistical significance of results similar to a 10-fold-cross-validation strategy.
+Figure~\ref{fig:classificationFroc} shows the FROC results for the trained networks including indicators for the standard deviation of the measurements.
+The detection identification rate denotes the amount of ground truth logos which are correctly detected and are assigned the correct brand.
+While the baseline is only able to find a minor amount of the logos, our best performing approach is able to correctly retrieve 25 percent of the logos if tolerating only one false alarm every 100 images.
+As expected, the more recent network architectures provide better results.
+Also, including the Logos in the Wild data in the training yields a significant boost in performance.
+Specifically, the larger training dataset has a larger impact on the performance than a better network architecture.
+%
+\begin{figure}%
+\centering%
+\includegraphics[width=\linewidth, trim=0cm 7cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
+\caption{Detection+Classification FROC curve for FlickrLogos32 test set. Including dashed indicators for one standard deviation.}%
+\label{fig:classificationFroc}
+\end{figure}%
+%
+%As far as we are aware, this is the first experiment with open set logo retrieval on 
+Table~\ref{tab:map} compares our open set results with closed set results from the literature in terms of the mean average precision (map). 
+%
+\begin{table}[t]
+\centering
+\begingroup	
+\setlength{\tabcolsep}{6pt}
+\caption{FlickrLogos32 test set retrieval results.}
+\label{tab:sportDataStatistics}
+\begin{small}
+% Table generated by Excel2LaTeX from sheet 'FlickrLogos32Test'
+\begin{tabular}{crc}
+\textbf{setting} & \multicolumn{1}{c}{\textbf{method}} & \textbf{map} \bigstrut[b]\\
+\hline
+\multirow{5}[2]{*}{\begin{sideways}open set\end{sideways}} & baseline~\cite{??} & 0,036 \bigstrut[t]\\
+      & VGG16 - public & 0,286 \\
+      & ResNet101 - public & 0,327 \\
+\cline{2-3}      
+      & VGG16 - public+LitW & 0,382 \bigstrut[t]\\
+      & ResNet101 - public+LitW & 0,464 \bigstrut[b]\\
+\hline
+\multirow{5}[1]{*}{\begin{sideways}closed set\end{sideways}} & \cite{??} & ?? \bigstrut[t]\\
+      & \cite{??} & ?? \\ %TODO cite values from literature
+      & \cite{??} & ?? \\
+      & \cite{??} & ?? \\
+      & \cite{??} & ?? \\
+\end{tabular}%
+\end{small}
+\endgroup
+\end{table}
+We achieve ?? percent of the closed set performance with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time.
 
@@
 \includegraphics[width=\linewidth]{img/football-1908719_1920_cut.jpg}%
-\caption{Example football frame with small logos in the perimeter advertising.}%
+\caption{Example football scene with small logos in the perimeter advertising.}%
 \label{fig:footballSample}

### 2017-09-01 paper-review.tex
Polishing.

@@
 \newacro{PCA}{Principle Component Analysis}
+\newacro{SIFT}{Scale Invariant Feature Transform}
+\newacro{SVM}{Support Vector Machine}
 
@@
 %
-\begin{figure}[!h]
+\begin{figure}[t]
   %\vspace{-0.2cm}
@@
 Especially, occlusions, blur and variations within a logo type are only partially covered.
-To address these shortcomings, a novel in-the-wild logo dataset is collected and made publicly available~\footnote{\url{url//:to.come}}.
+To address these shortcomings, a novel in-the-wild logo dataset is collected and made publicly available~\footnote{\url{url://to.come}}.
 
@@
 \section{\uppercase{Related Work}}
-\noindent- Logo Retrieval (\xie closed set approaches) \\
-Current logo retrieval strategies are generally solving a closed set detection and classification problem.
+%\noindent- Logo Retrieval (\xie closed set approaches) \\
+\noindent Current logo retrieval strategies are generally solving a closed set detection and classification problem.
 Eggert et.al.
-\cite{eggert2015} utilized convolutional neural network to extract features from logos and classified them with a set of SVMs to the target classes.
+\cite{eggert2015} utilized \acp{CNN} to extract features from logos and determined their brand by classification with a set of \acp{SVM}.
 Fast R-CNN \cite{girshick2015} was used for the first time to retrieve logos from images by Iandola et al.
@@
 Furthermore, R-CNN, Fast R-CNN and Faster R-CNN were used in \cite{bao2016}, \cite{oliveira2016}, \cite{qi2017}.
-All these works use the same classes for training as for validation.
+All these works use the same brands for training as for validation.
 
 %- Other retrieval applications (\xeg face, person)
+\subsection{Open Set Retrieval}
 Retrieval scenarios in other domains are basically always considered open set, \xie samples from the currently searched class have never been seen before.
-%, because the searched classes are rarely known beforehand. 
 This is the case for general purpose image retrieval~\cite{sivic2003}, tattoo retrieval~\cite{manger2012} or for person retrieval in image or video data where face or appearance-based methods are common~\cite{bauml2010,weber2011,herrmann2015b}.
 The reason is that these in-the-wild scenarios offer usually a too large and impossible to capture variety of object classes.
-In case of persons, a class would be an identity.
+In case of persons, a class would be a person identity with billions of persons existing.
 Consequently, methods have to be designed and trained on a limited set of classes and have to generalize to previously unseen classes.
 We argue that this approach is also required for logo retrieval because of the vast amount of existing brands and according logos which cannot be captured in advance.
+Typically, approaches targeting open set scenarios consist of an object detector and a feature extractor~\cite{??}.
+The detector localizes the objects of interest and the feature extractor creates a discriminative descriptor regarding the target classes which can than be compared to query samples.
 
 % Detector Frameworks: Faster R-CNN~\cite{ren2015}, SSD~\cite{liu2016b}, Yolo~\cite{redmon2016}, ...
-Earlier systems utilized hand-crafted features to detect objects on images and recognize them.
-Lowe et al., used Scale and Translation Invariant Features (SIFT) ~\cite{lowe2004} around keypoints, detected with e.g.
-Harris corner detector ~\cite{harris1988}.
-Viola and Jones utilized ~\cite{viola2004} Haar-like features and a cascade of weak classifiers (Adaptive Boosting ~\cite{schapire1999}) to detect faces extremely fast.
-Nowadays, deep learning methods surpass the traditional methods by a wide margin.
-OverFeat framework ~\cite{sermanet2013} uses sliding windows on multiple scales of the image, and combines the features to detect objects and to classify them.
-You Only Look Once (YOLO) ~\cite{redmon2015} introduces an end-to-end network for object detection and classification by using bounding box regressors for the first time for localization.
-It splits the input image into a square grid, where every cell predicts several bounding boxes with probability scores and classification labels.
-The Single Shot MultiBox Detector (SSD) \cite{liu2015} utilizes convolutional features from multiple layers and concatenates them to detect objects in real time.
-Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a region proposal network (RPN) to detect objects on feature maps and classifies the found regions by a fully connected network.
-Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b} is the improvement of Faster R-CNN in terms of inference time by having a network end-to-end fully convolutional.
-Mask R-CNN \cite{he2017} extends the functionality of Faster R-CNN by extending the network with a classification mask, which allows end-to-end object detection and semantic segmentation with a little overhead.
+\subsection{Object Detector Frameworks}
+Early detectors applied hand-crafted features, such as Haar-like features, combined with a classifier to detect objects in images \cite{viola2004}. 
+Nowadays, deep learning methods surpass the traditional methods by a significant margin.
+In addition, they allow a certain level of object classification within the detector which is mostly used to simultaneously detect different object categories \cite{sermanet2013}.
+%The OverFeat framework uses sliding windows on multiple scales of the image and combines the \ac{CNN} features to detect objects and classify them. 
+The YOLO detector \cite{redmon2015} introduces an end-to-end network for object detection and classification based on bounding box regressors for object localization.
+This concept is similarly applied by the Single Shot MultiBox Detector (SSD) \cite{liu2015}.
+Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a region proposal network (RPN) to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network.
+Improvements of the Faster R-CNN are the Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b}, which reduces inference time by an end-to-end fully convolutional network, and the Mask R-CNN \cite{he2017}, adding a classification mask for instance segmentation.
 
 % Classification Networks: AlexNet, VGG, ResNet, DenseNet
-AlexNet \cite{krizhevsky2012b} was the first neural network after the conquest of support vector machines, achieving impressive performance, and won the ImageNet challenge \cite{deng2009} in 2012.
-It consists of five convolutional layers, each followed by a max-pooling, which counted for a very deep network at that time.
+\subsection{\acs{CNN}-based Classification}
+AlexNet \cite{krizhevsky2012b} was the first neural network after the conquest of \acp{SVM}, achieving impressive performance on image content classification and winning the ImageNet challenge \cite{deng2009}.
+It consists of five convolutional layers, each followed by a max-pooling, which counted as a very deep network at the time.
 VGG \cite{simonyan2014} follows the general architecture of AlexNet with an increased number of convolutional layers achieving better performance. 
-Residual Networks (ResNet) \cite{he2015} utilizes very deep network architecture of 50-151 layers, and adopts skip connections, which is a direct connection from the output of a lower layer (the one lying closer to the input image).
-These connections address the problem of degradation, which arises when very deep networks are involved, causing performance dropping.
-DenseNet \cite{huang2016} has also a ResNet-like architecture, and introduces "dense units".
-The output of these units is connected with every subsequent dense unit's input with concatenation.
+The inception architecture~\cite{szegedy2015} proposed a multi-path network module for better multi-scale addressing, but was shortly after superseded by the Residual Networks (ResNet) \cite{he2015,he2016}.
+They increase network depth heavily up to 1000 layers in the most extreme configurations by additional skip connections which bypass two convolutional layers.
+The recent DenseNet \cite{huang2016} builds on a ResNet-like architecture and introduces ``dense units''.
+The output of these units is connected with every subsequent dense unit's input by concatenation.
 This results in a much denser network than a conventional feed-forward network.
@@
 \section{\uppercase{Logo Detection}}
-\noindent- class agnostic detector \\
-- different base networks: VGG-CNN-M, VGG16
+%\noindent- class agnostic detector \\
+%- different base networks: VGG-CNN-M, VGG16
 % TODO
-For scene retrieval it is conventional, that one feature is created for an input image.
-This is achieved either by inferring from the complete image or by searching for key regions and then extracting features from the found regions, which are finally fused into a global feature.
-For logo retrieval the goal is not the extraction of a global feature, because it would not be descriptive enough to retrieve small objects.
-Additionally, a global feature usually does not preserve information of the location and the size of the objects, which are also important factors for logo retrieval.
+\noindent The usual approach for scene retrieval is to create a global feature of the input image.
+This is achieved either by inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature.
+For logo retrieval, extraction of a global feature is counterproductive because it lacks discriminative power to retrieve small objects.
+Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval.
 
-Therefore, first the objects should be detected in the input image.
-There are a lot of possibilities to search for objects as explained in cha.
+Therefore, we choose a two-stage approach consisting of logo detection and logo classification as illustrated in figure~\ref{fig:pipeline}. First, the logos have to be detected in the input image. 
+There are a lot of options to search for objects as explained in cha.
 Girshick et al.
@@
 %%TODO Christian
-\noindent To train the proposed logo detector, a novel logo dataset is collected to supplement publicly available logo datasets.
+\noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets.
 A comparison to other datasets is given in table~\ref{tab:logoDatasets}.
@@
 Starting with a list of well-known brands and companies, an image web search is performed.
-Because most other web collected logo datasets mainly rely on Flickr, we choose to use Google image search to broaden the domain.
+Because most other web collected logo datasets mainly rely on Flickr, we opt for Google image search to broaden the domain.
 Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `bmw advertisement', `bmw building', `bmw poster' or `bmw store'.
@@
 %All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
-After removing duplicates, this results in 4~to 608~images per searched brand. These images are then one-by-one annotated with bounding boxes or sorted out if unsuitable.
+After removing duplicates, this results in 4~to 608~images per searched brand. These images are then one-by-one annotated with logo bounding boxes or sorted out if unsuitable.
 Images are considered unsuitable if they contain no logos or fail the in-the-wild requirement, which is the case for the original raw logo graphics.
@@
 150 brands occur at least 10 times.
-An image may contain more than one logo with the maximum being 100 logos in one image.
+An image may contain several logos with the maximum being 100 logos in one image.
 The complete distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}.
@@
 \section{\uppercase{Experiments}}
-\noindent- explain FROC curve \\
-- maybe introduce mAP \\
-- explain baseline method(s) \\
-concepts/desired experiments \\
-- train on public non-Flickr brands \\
-- additionally train on own logo dataset \\
-- test on FlickrLogos32 test datasets \\
-
-- additional evaluation on own SportsLogos dataset and qualitative results \\
-
-The proposed method is evaluated on the test set of the public FlickrLogos32 dataset including the distractors.
+%\noindent- explain FROC curve \\
+%- maybe introduce mAP \\
+%- explain baseline method(s) \\
+%concepts/desired experiments \\
+%- train on public non-Flickr brands \\
+%- additionally train on own logo dataset \\
+%- test on FlickrLogos-32 test datasets \\
+%
+%- additional evaluation on own SportsLogos dataset and qualitative results \\
+\noindent The proposed method is evaluated on the test set of the public FlickrLogos-32 dataset including the distractors.
 Additional experiments are performed on an internal dataset of sports event TV broadcasts.
-For a proper separation of train and test data, all brands which are present in the FlickrLogos32 test set are removed from the training data.
+For a proper separation of train and test data, all brands which are present in the FlickrLogos-32 test set are removed from the training data.
 The training set consists of two parts.
@@
 %- train 3 different detectors: multi-class Faster R-CNN (maybe RPN), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
-%- test on FlickrLogos32 => FROC plot\\
+%- test on FlickrLogos-32 => FROC plot\\
 %- test first two detectors on own logo dataset => FROC plot\\
@@
 \includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
-\caption{Detection FROC curve for FlickrLogos32 test set.}%
+\caption{Detection FROC curve for FlickrLogos-32 test set.}%
 \label{fig:detectionFroc}
@@
 %- describe repeated query logo strategy => 10 sample => mean + std
-%- results on FlickrLogos32 => FROC plot\\
+%- results on FlickrLogos-32 => FROC plot\\
 %- results on own sports data => FROC plot\\
@@
 
-In 10 iterations, each of the 10 FlickrLogos32 train samples for each brand serves as query sample.
+In 10 iterations, each of the 10 FlickrLogos-32 train samples for each brand serves as query sample.
 This allows to assess the statistical significance of results similar to a 10-fold-cross-validation strategy.
@@
 \includegraphics[width=\linewidth, trim=0cm 7cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
-\caption{Detection+Classification FROC curve for FlickrLogos32 test set. Including dashed indicators for one standard deviation.}%
+\caption{Detection+Classification FROC curve for FlickrLogos-32 test set. Including dashed indicators for one standard deviation.}%
 \label{fig:classificationFroc}
@@
 \setlength{\tabcolsep}{6pt}
-\caption{FlickrLogos32 test set retrieval results.}
-\label{tab:sportDataStatistics}
+\caption{FlickrLogos-32 test set retrieval results.}
+\label{tab:map}
 \begin{small}
-% Table generated by Excel2LaTeX from sheet 'FlickrLogos32Test'
+% Table generated by Excel2LaTeX from sheet 'FlickrLogos-32Test'
 \begin{tabular}{crc}

### 2017-09-03 dataset_preparation/create_clean_dataset.py
new results

@@ -1,0 +1,206 @@
+# -*- coding: iso-8859-1 -*-
+from shutil import copy2
+import shutil
+import os
+import xml.etree.ElementTree
+import cv2
+
+path = '/home/atuezkoe/data/datasets/LogoDataset_wo_fl32'
+ext = '.jpg'
+dstext = '.jpg'
+postfix = ''
+
+fuse_occluded = True
+
+imglist = ''
+brandlist = list()
+for r, subdirs, files in os.walk(path):
+    for filename in files:
+        if not filename.endswith('.xml'):
+            continue
+
+        filewithpath = os.path.join(r, filename)
+        parent = filewithpath.split('/')[-2]
+        parser = xml.etree.ElementTree.XMLParser(encoding="utf-8")
+        tree = xml.etree.ElementTree.parse(filewithpath, parser = parser)
+        root = tree.getroot()
+
+        imagename = filename.split('.')[0]
+
+        imglist += parent + imagename + postfix + '\n'
+
+
+
+
+
+        for obj in root.findall('object'):
+            brand = obj.find('name').text.encode('utf-8').lower()
+            if brand == "aluratek":
+                brand = "aluratek-symbol"
+            if brand == "apecase":
+                brand = "apecase-symbol"
+            if brand == "apecase-teilsichtbar":
+                brand = "apecase-symbol-teilsichtbar"
+            if brand == "armitron1":
+                brand = "armitron"
+            if brand == "audi":
+                brand = "audi-symbol"
+            if brand == "b":
+                brand = "bridgestone"
+            if brand == "basf-symbol":
+                brand = "basf"
+            if "bertha1" in brand:
+                brand = brand.replace("bertha1", "bertha")
+            if "boing" in brand:
+                brand = brand.replace("boing", "boeing")
+            if "budweiser1" in brand:
+                brand = brand.replace("budweiser1", "budweiser")
+            if "budweiser2" in brand:
+                brand = brand.replace("budweiser2", "budweiser")
+            if brand == "budweiser-b":
+                brand = "budweiser-b-symbol"
+            if brand == "budweiser-teilsichtbar":
+                brand = "budweiser-symbol-teilsichtbar"
+            if "bundweiser" in brand:
+                brand = brand.replace("bundweiser", "budweiser")
+            if brand == "burgerking":
+                brand = "burgerking-symbol"
+            if brand == "burgerking-teilsichtbar":
+                brand = "burgerking-symbol-teilsichtbar"
[…]

### 2017-09-03 dataset_preparation/xml_to_rois.py

@@ -1,0 +1,252 @@
+# -*- coding: iso-8859-1 -*-
+from shutil import copy2
+import shutil
+import os
+import xml.etree.ElementTree
+import cv2
+
+path = '/Volumes/WD/logodata'
+ext = '.jpg'
+dstext = '.jpg'
+postfix = '_det'
+
+skip_occluded = True
+
+fuse_occluded = True
+
+outpath = os.path.join(path, '..', 'processed', 'data')
+
+annotationspath = os.path.join(outpath, 'Annotations')
+imagespath = os.path.join(outpath, 'Images')
+imagesetspath = os.path.join(outpath, 'ImageSets')
+brandspath = os.path.join(outpath, 'brands')
+
+if os.path.exists(outpath):
+    shutil.rmtree(outpath)
+
+os.makedirs(annotationspath)
+os.makedirs(imagespath)
+os.makedirs(imagesetspath)
+
+imglist = ''
+brandlist = list()
+subdirID = 0
+dirs = None
+for r, subdirs, files in os.walk(path):
+    if dirs == None:
+        dirs = subdirs
+    #parent = dirs[subdirID]
+    subdirID += 1
+    for filename in files:
+        if not filename.endswith('.xml'):
+            continue
+
+        filewithpath = os.path.join(r, filename)
+        parent = filewithpath.split('/')[-2]
+        parser = xml.etree.ElementTree.XMLParser(encoding="utf-8")
+        root = xml.etree.ElementTree.parse(filewithpath, parser = parser).getroot()
+
+        imagename = filename.split('.')[0]
+
+        imglist += parent + '_' + imagename + postfix + '\n'
+
+        #with open(os.path.join(annotationspath, parent + "_" + imagename + postfix + dstext + '.bboxes.txt'), 'w') as annotfile:
+        im = cv2.imread(os.path.join(r, imagename + ext))
+        print(os.path.join(r, imagename + ext))
+        i = 0
+        for obj in root.findall('object'):
+            brand = obj.find('name').text.encode('utf-8').lower()
+            if brand == "1fcköln":
+                brand = "fckoeln"
+            if brand == "aluratek":
+                brand = "aluratek-symbol"
+            if brand == "apecase":
+                brand = "apecase-symbol"
+            if brand == "apecase-teilsichtbar":
+                brand = "apecase-symbol-teilsichtbar"
+            if brand == "armitron1":
+                brand = "armitron"
+            if brand == "audi":
+                brand = "audi-symbol"
[…]

### 2017-09-04 paper-review.tex
new results
Updated retrieval figures.

@@
 \newacro{HOG}{Histogram of Oriented Gradients}
+\newacro{LitW}{Logos in the Wild}
 \newacro{PCA}{Principle Component Analysis}
@@
 \newcommand{\mne}{\mathit{MNE}}
-\newcommand{\map}{\mathit{map}}
+\newcommand{\map}{$\mathit{map}$}
 \newcommand{\acc}{\mathit{acc}}
@@
 %%TODO write text here, 70-200 words
-%motivation:	open set logo retrieval for broadcast analysis, \xeg to judge advertisement effectiveness 
-%problem: search for unknown logo classes; find all occurrences of a query logo; challenges: geometric distortions, different types
-%approach: two stage concept with detection and comparison, both using a \ac{CNN}, similar to the concept used in other retrieval tasks
-%results: general purpose logo detection yields viable results
-%conclusion: 
-%%
-Searching for logos in image data allows several applications, with judging the effectiveness of advertisement in sports event broadcasts being one example.
+Current logo retrieval research focuses on closed set scenarios.
+We argue that the logo domain is too large for this strategy and requires an open set approach.
+To foster research in this direction, the large-scale Logos in the Wild dataset is collected and released to the public.
+Searching for logos in image data has many applications, with judging the effectiveness of advertisement in sports event broadcasts being one example.
 Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a database of images or videos.
 Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption.
-To address this issue, an open set logo retrieval method is proposed in this work which can search for previously unfamiliar logos only by one query sample.
-A two stage concept with an open set logo detection and comparison is proposed similar to other retrieval tasks.
+To address this issue, an open set logo retrieval method is proposed in this work which allows search for previously unfamiliar logos only by one query sample.
+A two stage concept with an open set logo detection and comparison is proposed.
 Both modules are based on task specific \acp{CNN}.
-To train the detector with appropriate in-the-wild data, an according novel Logos in the Wild dataset is collected and made publicly available.
-The proposed method extends the application field in comparison to closed set approaches and improvements over baseline methods derived from these state-of-the-art closed set approaches are shown.
+The novel Logos in the Wild dataset serves to train the modules with sufficient appropriate in-the-wild data.
+The proposed method extends the application field in comparison to closed set approaches and significant improvements over baseline methods derived from these state-of-the-art closed set approaches are shown.
 }
@@
 One challenge for training a general purpose logo detector lies in appropriate training data.
-Many logo or trademark dataset~\cite{eakins1998,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application.
+Many logo or trademark dataset~\cite{eakins1998,hoi2015,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application.
 The need for annotated logo bounding boxes in the images limits the number of suitable datasets.
@@
 % TODO
-\noindent The usual approach for scene retrieval is to create a global feature of the input image.
+\noindent The current state-of-the-art approach for scene retrieval is to create a global feature of the input image.
 This is achieved either by inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature.
@@
 This network has a bounding box regressor for each trained class, thus it is capable to produce object type specific region proposals.
+
+% Logo comparison and classification can be included in the Faster R-CNN framework at the cost of generalization to unseen classes.
+We argue that specialization to a few dozen specific brands does not cover the complexity and breadth of the domain.
 
@@
 \noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets.
-A comparison to other datasets is given in table~\ref{tab:logoDatasets}.
+A comparison to other public in-the-wild datasets with annotated bounding boxes is given in table~\ref{tab:logoDatasets}.
 %
@@
 \centering
-\caption{Publicly available logo datasets in comparison with the novel dataset.}
+\caption{Publicly available in-the-wild logo datasets in comparison with the novel dataset.}
 \label{tab:logoDatasets}
@@
 %- additional evaluation on own SportsLogos dataset and qualitative results \\
-\noindent The proposed method is evaluated on the test set of the public FlickrLogos-32 dataset including the distractors.
-Additional experiments are performed on an internal dataset of sports event TV broadcasts.
-For a proper separation of train and test data, all brands which are present in the FlickrLogos-32 test set are removed from the training data.
+\noindent The proposed method is evaluated on the test set benchmark of the public FlickrLogos-32 dataset including the distractors.
+Additional application specific experiments are performed on an internal dataset of sports event TV broadcasts.
 The training set consists of two parts.
-The union of all public logo datasets and the novel Logos in the Wild dataset.
-The respective training and test set sizes are listed in table~\ref{tab:trainData}.
+The union of all public logo datasets as listed in table~\ref{tab:logoDatasets} and the novel \ac{LitW} dataset.
+For a proper separation of train and test data, all brands which are present in the FlickrLogos-32 test set are removed from the public and \ac{LitW} data.
+10 percent of the remaining images are set aside for network validation in each case.
+This results in the final training and test set sizes listed in table~\ref{tab:trainTestStatistics}.
 %
@@
 \begin{small}
-\begin{tabular}{l|c}
-?? & ?? %TODO
-\end{tabular}
+% Table generated by Excel2LaTeX from sheet 'Tabelle1'
+\begin{tabular}{cl|rr}
+\textbf{phase} & \multicolumn{1}{c|}{\textbf{data}} & \multicolumn{1}{c}{\textbf{brands}} & \multicolumn{1}{c}{\textbf{RoIs}} \bigstrut[b]\\
+\hline
+\multirow{2}[2]{*}{train} & public & 47    & 3.113 \bigstrut[t]\\
+      & public+\ac{LitW} & 632   & 18.960 \bigstrut[b]\\
+\hline
+test  & FlickrLogos-32 test & 32    & 1.602 \bigstrut[t]\\
+\end{tabular}%
 \end{small}
@@
 %%TODO write text here
-As baseline, the state-of-the-art closed set logo retrieval method from~\cite{??} is employed and trained on the public portion of the training data.
+As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
 It is adapted to open set detection by using the RPN scores as detections.
@@
 \includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
-\caption{Detection FROC curve for FlickrLogos-32 test set.}%
+\caption{Detection FROC curves for FlickrLogos-32 test set.}%
 \label{fig:detectionFroc}
@@
 Further improvement is achieved by combining the public training data with the novel data.
-Adding the Logos in the Wild dataset as additional training data improves the detection results with its large variety of additional training brands. 
+Adding \ac{LitW} as additional training data improves the detection results with its large variety of additional training brands. 
 This confirms findings from other domains, such as face analysis, where wider training datasets are preferred over deeper ones~\cite{bansal2017}.
@@
 Descriptor matching is performed in all cases with cosine similarity.
-Three different state-of-the-art classification architectures, namely VGG16~\cite{simonyan2014}, ResNet101~\cite{he2015} and DenseNet??~\cite{huang2016}, serve as base for the logo classification stage.
-All networks are pretrained on ImageNet and afterwards fine-tuned either on the public logo train set or the combination of the public and the Logos in the Wild train data.
+Three different state-of-the-art classification architectures, namely VGG16~\cite{simonyan2014}, ResNet101~\cite{he2015} and DenseNet161~\cite{huang2016}, serve as base for the logo classification stage.
+All networks are pretrained on ImageNet and afterwards fine-tuned either on the public logo train set or the combination of the public and the \ac{LitW} train data.
 
+\subsubsection*{FlickrLogos-32}
+\vspace*{-2.5mm}
 In 10 iterations, each of the 10 FlickrLogos-32 train samples for each brand serves as query sample.
@@
 As expected, the more recent network architectures provide better results.
-Also, including the Logos in the Wild data in the training yields a significant boost in performance.
+Also, including the \ac{LitW} data in the training yields a significant boost in performance.
 Specifically, the larger training dataset has a larger impact on the performance than a better network architecture.
@@
 \includegraphics[width=\linewidth, trim=0cm 7cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
-\caption{Detection+Classification FROC curve for FlickrLogos-32 test set. Including dashed indicators for one standard deviation.}%
+\caption{Detection+Classification FROC curves for FlickrLogos-32 test set.
+Including dashed indicators for one standard deviation.
+DenseNet results are omitted for clarity, refer to table~\ref{tab:mapFlickr} for full results.}%
 \label{fig:classificationFroc}
@@
 %As far as we are aware, this is the first experiment with open set logo retrieval on 
-Table~\ref{tab:map} compares our open set results with closed set results from the literature in terms of the mean average precision (map). 
+Table~\ref{tab:mapFlickr} compares our open set results with closed set results from the literature in terms of the mean average precision (\map). 
 %
@@
 \caption{FlickrLogos-32 test set retrieval results.}
-\label{tab:map}
+\label{tab:mapFlickr}
 \begin{small}
@@
 \begin{tabular}{crc}
-\textbf{setting} & \multicolumn{1}{c}{\textbf{method}} & \textbf{map} \bigstrut[b]\\
+\textbf{setting} & \multicolumn{1}{c}{\textbf{method}} & \textbf{\map} \bigstrut[b]\\
 \hline
-\multirow{5}[2]{*}{\begin{sideways}open set\end{sideways}} & baseline~\cite{??} & 0,036 \bigstrut[t]\\
-      & VGG16 - public & 0,286 \\
-      & ResNet101 - public & 0,327 \\
+\multirow{7}[2]{*}{\begin{sideways}open set\end{sideways}} & baseline, public~\cite{su2016} & 0.036 \bigstrut[t]\\
+      & VGG16, public & 0.286 \\
+      & ResNet101, public & 0.327 \\
+      & DenseNet161, public & 0.368 \\
 \cline{2-3}      
-      & VGG16 - public+LitW & 0,382 \bigstrut[t]\\
-      & ResNet101 - public+LitW & 0,464 \bigstrut[b]\\
+      & VGG16, public+\ac{LitW} & 0.382 \bigstrut[t]\\
+      & ResNet101, public+\ac{LitW} & \textbf{0.464} \\
+      & DenseNet161, public+\ac{LitW} & 0.448  \bigstrut[b]\\      
 \hline
-\multirow{5}[1]{*}{\begin{sideways}closed set\end{sideways}} & \cite{??} & ?? \bigstrut[t]\\
-      & \cite{??} & ?? \\ %TODO cite values from literature
-      & \cite{??} & ?? \\
-      & \cite{??} & ?? \\
-      & \cite{??} & ?? \\
+\multirow{4}[1]{*}{\begin{sideways}closed set\end{sideways}} & BD-FRCN-M \cite{oliveira2016} & 0.735 \bigstrut[t]\\	
+      & DeepLogo \cite{iandola2015} & 0.744 \\ 
+      & Faster-RCNN \cite{su2016} & 0.811 \\
+      & Fast-M \cite{bao2016} & \textbf{0.842} \\
 \end{tabular}%
@@
 \end{table}
-We achieve ?? percent of the closed set performance with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time.
+We achieve more than half of the closed set performance in terms of \map with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time.
+In addition, our approach is not limited to the 32 FlickrLogos brands but generalizes with a similar performance to further brands.
+In contrast, the closed-set approaches hardly generalize as is shown by the baseline open set method.
+This is the second best closed set approach only retrained on out-of-test brands.
 
+\subsubsection*{SportsLogos}
+\vspace*{-2.5mm}
 In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events.
-In total, 1,218 annotated frames with more than 10,000 logos from four different events are available in our SportLogo dataset where 3 events are used for training and one as test set.
+In total, 1,218 annotated frames with more than 10,000 logos from four different events are available in our SportsLogos dataset where 3 events are used for training and one as test set.
 Refer to table~\ref{tab:sportDataStatistics} for details.
 In comparison to public logo datasets, the logos are usually significantly smaller in these cases and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}.
+Consequently, the results in this real world scenario as indicated in figure~\ref{fig:classificationFrocFootball} are slightly worse than in the FlickrLogos-32 benchmark.
+Nevertheless, training with \ac{LitW} data again improves the results significantly.
 %
@@
 %
-
 %Due to copyright reasons this internal dataset cannot be made publicly available.
@@
 \setlength{\tabcolsep}{5pt}
-\caption{SportLogo dataset statistics.}
+\caption{SportsLogos dataset statistics.}
 \label{tab:sportDataStatistics}
@@
 \end{table}
+%
+\begin{figure}%
+\centering%
+\includegraphics[width=\linewidth, trim=0cm 7cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
+\caption{Detection+Classification FROC curve for SportsLogos test set. \map is given in brackets.}%
+\label{fig:classificationFrocFootball}
+\end{figure}%
+%
 

### 2017-09-05 dataset_preparation/create_clean_dataset.py
schalke results, dataset cleaner almost ready

@@ -4,203 +4,556 @@ import shutil
 import os
 import xml.etree.ElementTree
 import cv2
+import argparse
 
-path = '/home/atuezkoe/data/datasets/LogoDataset_wo_fl32'
+
 ext = '.jpg'
 dstext = '.jpg'
 postfix = ''
 
-fuse_occluded = True
+fl32_intersection = ["adidas-text", "adidas1", "adidas2", "adidas3", "aldi", "aldi-text", "aldinord", "apple",
+                     "becks", "becks-symbol", "bmw", "carlsberg", "coca-cola", "coke", "corona-text", "corona-symbol",
+                     "dhl", "esso", "esso-text", "federalexpress", "fedex", "ferrari", "ford-symbol", "google-text",
+                     "google+", "google-symbol", "guinness", "heineken", "hp", "milka", "nvidia", "paulaner",
+                     "pepsi-text", "pepsi-symbol", "shell-symbol", "shell-text", "starbucks-text", "starbucks-symbol",
+                     "stellaartois", "tsingtao", "ups"]
 
-imglist = ''
-brandlist = list()
-for r, subdirs, files in os.walk(path):
-    for filename in files:
-        if not filename.endswith('.xml'):
-            continue
+def parse_args():
+    """
+    Parse input arguments
+    """
+    parser = argparse.ArgumentParser(description='Test a Fast R-CNN network')
+    parser.add_argument('--in', dest='inpath', help='Path of the original dataset to be cleaned. It won\'t be modified.',
+                        default=None, type=str, required=True)
+    parser.add_argument('--out', dest='outpath',
+                        help='Path where the cleaned dataset will be copied.',
+                        default=None, type=str, required=True)
+    parser.add_argument('--wofl32', dest='wofl32',
+                    help='Generate the dataset without the classes of FlickrLogos32.',
+                    action='store_true', default=False)
+    parser.add_argument('--roi', dest='roi',
+                    help='Writes the rois out for each brands separately.',
+                    action='store_true', default=False)
 
-        filewithpath = os.path.join(r, filename)
-        parent = filewithpath.split('/')[-2]
-        parser = xml.etree.ElementTree.XMLParser(encoding="utf-8")
-        tree = xml.etree.ElementTree.parse(filewithpath, parser = parser)
-        root = tree.getroot()
-
-        imagename = filename.split('.')[0]
-
-        imglist += parent + imagename + postfix + '\n'
+    parser.add_argument('--commonformat', dest='commonformat',
[…]

### 2017-09-05 dataset_preparation/xml_to_rois.py

@@ -1,252 +1,0 @@
-# -*- coding: iso-8859-1 -*-
-from shutil import copy2
-import shutil
-import os
-import xml.etree.ElementTree
-import cv2
-
-path = '/Volumes/WD/logodata'
-ext = '.jpg'
-dstext = '.jpg'
-postfix = '_det'
-
-skip_occluded = True
-
-fuse_occluded = True
-
-outpath = os.path.join(path, '..', 'processed', 'data')
-
-annotationspath = os.path.join(outpath, 'Annotations')
-imagespath = os.path.join(outpath, 'Images')
-imagesetspath = os.path.join(outpath, 'ImageSets')
-brandspath = os.path.join(outpath, 'brands')
-
-if os.path.exists(outpath):
-    shutil.rmtree(outpath)
-
-os.makedirs(annotationspath)
-os.makedirs(imagespath)
-os.makedirs(imagesetspath)
-
-imglist = ''
-brandlist = list()
-subdirID = 0
-dirs = None
-for r, subdirs, files in os.walk(path):
-    if dirs == None:
-        dirs = subdirs
-    #parent = dirs[subdirID]
-    subdirID += 1
-    for filename in files:
-        if not filename.endswith('.xml'):
-            continue
-
-        filewithpath = os.path.join(r, filename)
-        parent = filewithpath.split('/')[-2]
-        parser = xml.etree.ElementTree.XMLParser(encoding="utf-8")
-        root = xml.etree.ElementTree.parse(filewithpath, parser = parser).getroot()
-
-        imagename = filename.split('.')[0]
-
-        imglist += parent + '_' + imagename + postfix + '\n'
-
-        #with open(os.path.join(annotationspath, parent + "_" + imagename + postfix + dstext + '.bboxes.txt'), 'w') as annotfile:
-        im = cv2.imread(os.path.join(r, imagename + ext))
-        print(os.path.join(r, imagename + ext))
-        i = 0
-        for obj in root.findall('object'):
-            brand = obj.find('name').text.encode('utf-8').lower()
-            if brand == "1fcköln":
-                brand = "fckoeln"
-            if brand == "aluratek":
-                brand = "aluratek-symbol"
-            if brand == "apecase":
-                brand = "apecase-symbol"
-            if brand == "apecase-teilsichtbar":
-                brand = "apecase-symbol-teilsichtbar"
-            if brand == "armitron1":
-                brand = "armitron"
-            if brand == "audi":
-                brand = "audi-symbol"
[…]

### 2017-09-05 dataset_preparation/create_clean_dataset.py
dataset cleaner update, litw further stat

@@ -73,6 +73,7 @@ if __name__ == '__main__':
                 print('Processed: ' + str(i) + ' images.')
             filewithpath = os.path.join(r, filename)
             parent = filewithpath.split('/')[-2]
+            parent = parent.replace(' ', '')
             parser = xml.etree.ElementTree.XMLParser(encoding="utf-8")
             tree = xml.etree.ElementTree.parse(filewithpath, parser = parser)
             root = tree.getroot()
@@ -344,6 +345,7 @@ if __name__ == '__main__':
                 if brand == "coke1":
                     brand = "coke"
                 if brand == "copyofamcrest-symbol":
+                    imagebrands.append('')
                     continue
                 if brand == "corona":
                     brand = "corona-text"
@@ -533,6 +535,9 @@ if __name__ == '__main__':
             for obj in root.findall('object'):
                 
                 brand = imagebrands[roiCounter]
+                roiCounter += 1
+                if brand == '':
+                    continue
                 
                 bndbox = obj.find('bndbox')
                 x1 = int(bndbox[0].text)
@@ -545,7 +550,6 @@ if __name__ == '__main__':
                 if args.commonformat:                
                     with open(os.path.join(annotationspath, parent + "_" + imagename + postfix + dstext + '.bboxes.txt'), 'a') as annotfile:
                         annotfile.write(str(x1) + ' ' + str(y1) + ' ' + str(x2) + ' ' + str(y2) + ' ' + brand + '\n')
-                roiCounter += 1
             if args.commonformat:
                 copy2(os.path.join(r, imagename + ext), os.path.join(imagespath, parent + '_' + imagename + postfix + dstext))
 
@@ -553,7 +557,7 @@ if __name__ == '__main__':
         with open(os.path.join(imagesetspath, 'litw' + postfix + '.txt'), 'w') as f:
             f.write(imglist)
 
-    with open(os.path.join(outpath, 'brands.txt'), 'w') as f:
+    with open(os.path.join(args.outpath, 'brands.txt'), 'w') as f:
         for brand in set(brandlist):
             f.write(brand + '\n')
 

### 2017-09-05 dataset_preparation/create_clean_dataset.py
Updated dataset statistics.

@@ -63,6 +63,9 @@ if __name__ == '__main__':
         os.makedirs(imagesetspath)
 
     i = 0
+    unavailableCounter = 0
+    imageCounter = 0
+    totalRoiCounter = 0
     print('Processing dataset files')
     for r, subdirs, files in os.walk(xmlpath):
         for filename in files:
@@ -71,17 +74,27 @@ if __name__ == '__main__':
                 continue
             if i % 1000 == 0:
                 print('Processed: ' + str(i) + ' images.')
+            imagename = filename.split('.')[0]
+            imgpath = os.path.join(r, imagename + ext)
             filewithpath = os.path.join(r, filename)
-            parent = filewithpath.split('/')[-2]
+            if not os.path.isfile(imgpath):
+                os.remove(filewithpath)
+                unavailableCounter += 1
+                print('Deleted xml for unavailable image file {:s}'.format(imgpath))
+                continue
+            imageCounter += 1
+            try:
+                parent = filewithpath.split('/')[-2]
+            except IndexError:
+                parent = filewithpath.split('\\')[-2]
             parser = xml.etree.ElementTree.XMLParser(encoding="utf-8")
             tree = xml.etree.ElementTree.parse(filewithpath, parser = parser)
             root = tree.getroot()
 
-            imagename = filename.split('.')[0]
-
             imglist += parent + imagename + postfix + '\n'
             roiCounter = 0
             im = cv2.imread(os.path.join(r, imagename + ext))
+            assert im is not None
             imagebrands = []
             intersection = False
             for obj in root.findall('object'):
@@ -523,7 +536,8 @@ if __name__ == '__main__':
                     if not os.path.exists(folder):
                         os.makedirs(folder)
                     cv2.imwrite(os.path.join(folder, roiname + '.jpg'), roi)
-                roiCounter += 1
+                roiCounter += 1                
+                totalRoiCounter += 1
 
             tree.write(filewithpath, encoding="UTF-8")
 
@@ -531,6 +545,10 @@ if __name__ == '__main__':
                 continue
             roiCounter = 0
             for obj in root.findall('object'):
+                                
+                labelBrand = obj.find('name').text.encode('utf-8').lower()
+                if labelBrand == 'copy of amcrest-logo':
+                    continue                
                 
                 brand = imagebrands[roiCounter]
                 
[…]

### 2017-09-05 dataset_preparation/getDatasetStatistics.py

@@ -1,0 +1,74 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Aug 23 14:17:58 2017
+
+@author: herrma
+"""
+
+#import os
+import xmltodict
+import numpy as np
+from dirRecursive import dirRecursive
+
+path = '~/LogoData-cleaned/voc_format'
+xmlFiles = dirRecursive(path, '*.xml')
+
+print('Annotated images: {:d}'.format(len(xmlFiles)))
+
+nBoxes = 0
+maxBoxes = 0
+boxesList = []
+brands = {}
+fullBrandList = np.empty(0,dtype='S')
+for xmlPath in xmlFiles:        
+    ### read ground truth bounding boxes
+    with open(xmlPath) as fx:
+        annot = xmltodict.parse(fx.read())
+        
+    # get object list
+    objects = annot['annotation']['object']    
+    if not isinstance(objects, list):
+        objects = [objects]
+    
+    # number of annotated objects
+    nBoxes += len(objects)
+    if len(objects) > maxBoxes:
+        maxBoxes = len(objects)
+    boxesList.append(len(objects))
+    
+    # collect classes of annotated objects
+    subPath = '/'.join(xmlPath.split('\\')[-2:])
+    for obj in objects:
+        if obj['name'] in brands:
+            brands[obj['name']][subPath] = 1
+        else:
+            brands[obj['name']] = {subPath:1}
+        fullBrandList = np.append(fullBrandList, obj['name'])
+            
+sortedBrands = [(key, brands[key]) for key in sorted(brands)]
+
+# frequency analysis and backreferences
+brand,freq = np.unique(fullBrandList, return_counts=True)
+# sort by frequency
+idx = np.argsort(-freq)
+brandFreq = [(brand[i],freq[i]) for i in idx]
+# sort by name 
+brandLow = np.core.defchararray.lower(brand)
+idx = np.argsort(brandLow)
+brandName = [(brandLow[i],freq[i]) for i in idx]
+
+# some lists for manual inspection and reference
+uniqueBrands = np.unique(np.array([s.split('-')[0] for s in brandLow]))
+uniqueSpecifiers = np.unique(np.array(['-'.join(s.split('-')[1:]) if len(s.split('-')) > 1 else 'none' for s in brandLow]))
+
+# file output
+np.savetxt('brandFreq.csv', freq, fmt='%d')
+np.savetxt('boxesPerImage.csv', np.asarray(boxesList), fmt='%d')
+
[…]

### 2017-09-05 paper-review.tex
schalke results, dataset cleaner almost ready
Updated dataset statistics.
DIR SportsLogos update.

@@
 Improvements of the Faster R-CNN are the Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b}, which reduces inference time by an end-to-end fully convolutional network, and the Mask R-CNN \cite{he2017}, adding a classification mask for instance segmentation.
+%
+\begin{figure*}%
+\centering%
+\includegraphics[width=\linewidth, trim=0cm 5cm 0cm 0cm, clip]{img/openset.pdf}%
+\caption{Comparison of closed and open set logo retrieval strategy.}%
+\label{fig:openClosedSet}
+\end{figure*}%
 
@@
 \cline{2-5}
-& total & 80 (union) & 15,598 & 23,222 \bigstrut \\
+& combined & 80 (union) & 15,598 & 23,222 \bigstrut \\
 \hline
-\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 631 & 6,084 & 17,738 \bigstrut[t]
+%\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 868 & 11,039 & 32,808 \bigstrut[t]
+\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 872 & 11,054 & 32,850 \bigstrut[t]
 \end{tabular}
@@
 Because most other web collected logo datasets mainly rely on Flickr, we opt for Google image search to broaden the domain.
-Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `bmw advertisement', `bmw building', `bmw poster' or `bmw store'.
+Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `advertisement', `building', `poster' or `store'.
 
@@
 %All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
-After removing duplicates, this results in 4~to 608~images per searched brand. These images are then one-by-one annotated with logo bounding boxes or sorted out if unsuitable.
+After removing duplicates, this results in 4~to 574~images per searched brand. These images are then one-by-one manually annotated with logo bounding boxes or sorted out if unsuitable.
 Images are considered unsuitable if they contain no logos or fail the in-the-wild requirement, which is the case for the original raw logo graphics.
@@
 %
-Altogether, the current version of the dataset, which is used in this paper, contains 631 brands with 17,738 annotated bounding boxes.
-150 brands occur at least 10 times.
-An image may contain several logos with the maximum being 100 logos in one image.
+Altogether, the current version of the dataset, which is used in this paper, contains 872 brands with 32,850 annotated bounding boxes.
+238 brands occur at least 10 times.
+An image may contain several logos with the maximum being 118 logos in one image.
 The complete distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}.
@@
 % Table generated by Excel2LaTeX from sheet 'Tabelle1'
-\begin{tabular}{cl|rr}
+\begin{tabular}{cl|cc}
 \textbf{phase} & \multicolumn{1}{c|}{\textbf{data}} & \multicolumn{1}{c}{\textbf{brands}} & \multicolumn{1}{c}{\textbf{RoIs}} \bigstrut[b]\\
@@
 As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
-It is adapted to open set detection by using the RPN scores as detections.
-This skips the closed set classification part of the network which is pre-trained on different logos than should be detected on the test set.
+It is naively adapted to open set detection by using the RPN scores as detections.
+This skips the closed set classification part of the network which is trained on different logos than should be detected on the test set.
 %Because of the closed set training strategy, only brands occurring in the training set are the final outcome of this detector. 
@@
 %
-For the retrieval experiments, the state-of-the-art closed set logo retrieval method from the previous section is again used as baseline.
-The class probabilities are interpreted as feature vector which is then used to match previously unseen logos.
+For the retrieval experiments, the Faster R-CNN based state-of-the-art closed set logo retrieval method from the previous section is again used as baseline.
+Now the full network is applied and the logo class probabilities are interpreted as feature vector which is then used to match previously unseen logos.
 For the proposed open set strategy, the best logo detection network from the previous section is used in all cases.
@@
 The detection identification rate denotes the amount of ground truth logos which are correctly detected and are assigned the correct brand.
-While the baseline is only able to find a minor amount of the logos, our best performing approach is able to correctly retrieve 25 percent of the logos if tolerating only one false alarm every 100 images.
+While the baseline method is only able to find a minor amount of the logos, our best performing approach is able to correctly retrieve 25 percent of the logos if tolerating only one false alarm every 100 images.
 As expected, the more recent network architectures provide better results.
@@
 \multirow{7}[2]{*}{\begin{sideways}open set\end{sideways}} & baseline, public~\cite{su2016} & 0.036 \bigstrut[t]\\
-      & VGG16, public & 0.286 \\
-      & ResNet101, public & 0.327 \\
-      & DenseNet161, public & 0.368 \\
+      & \textit{VGG16, public} & 0.286 \\
+      & \textit{ResNet101, public} & 0.327 \\
+      & \textit{DenseNet161, public} & 0.368 \\
 \cline{2-3}      
-      & VGG16, public+\ac{LitW} & 0.382 \bigstrut[t]\\
-      & ResNet101, public+\ac{LitW} & \textbf{0.464} \\
-      & DenseNet161, public+\ac{LitW} & 0.448  \bigstrut[b]\\      
+      & \textit{VGG16, public+\ac{LitW}} & 0.382 \bigstrut[t]\\
+      & \textit{ResNet101, public+\ac{LitW}} & \textbf{0.464} \\
+      & \textit{DenseNet161, public+\ac{LitW}} & 0.448  \bigstrut[b]\\      
 \hline
@@
 \end{table}
-We achieve more than half of the closed set performance in terms of \map with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time.
+We achieve more than half of the closed set performance in terms of \map~with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time.
 In addition, our approach is not limited to the 32 FlickrLogos brands but generalizes with a similar performance to further brands.
@@
 In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events.
-In total, 1,218 annotated frames with more than 10,000 logos from four different events are available in our SportsLogos dataset where 3 events are used for training and one as test set.
-Refer to table~\ref{tab:sportDataStatistics} for details.
+In total, this SportsLogos test set includes 298 annotated frames with 2,348 logos of 40 brands.
 In comparison to public logo datasets, the logos are usually significantly smaller in these cases and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}.
-Consequently, the results in this real world scenario as indicated in figure~\ref{fig:classificationFrocFootball} are slightly worse than in the FlickrLogos-32 benchmark.
-Nevertheless, training with \ac{LitW} data again improves the results significantly.
+Besides perimeter advertising, logos on clothing or equipment of the athletes and TV station or program overlays are the most occurring logo types.
+Overall, the results in this application scenario are slightly worse than in the FlickrLogos-32 benchmark with a drop in \map~from 0.464 to 0.354 for the best performing method, as indicated in figure~\ref{fig:classificationFrocFootball}.
+The baseline approach takes the largest performance hit showing that closed set approaches not only generalize badly to unseen logos but also to novel domains.
+In contrast, the proposed open set strategy shows a relatively stable cross-domain performance.
+Training with \ac{LitW} data again improves the results significantly.
 %
@@
 %
-\begin{table}[t]
-\centering
-\begingroup	
-\setlength{\tabcolsep}{5pt}
-\caption{SportsLogos dataset statistics.}
-\label{tab:sportDataStatistics}
-\begin{small}
-\begin{tabular}{l|cccc}
- & \textbf{phase} & \textbf{brands} & \sizebox{1.0cm}{\textbf{logo images}} & \textbf{RoIs} \bigstrut[b]\\
-\hline
-football-1 & \multirow{3}{*}{train} & {104} & {331} & {3,329} \bigstrut[t]\\
-{ski} & & {27} & {179} & {701} \\
-{ice hockey} & & {19} & {410} & {3,920} \bigstrut[b]\\
-\hline
-{football-2} & test & 40 & 298 & 2,348 \bigstrut\\
+%\begin{table}[t]
+%\centering
+%\begingroup	
+%\setlength{\tabcolsep}{5pt}
+%\caption{SportsLogos dataset statistics.}
+%\label{tab:sportDataStatistics}
+%\begin{small}
+%\begin{tabular}{l|cccc}
+% & \textbf{phase} & \textbf{brands} & \sizebox{1.0cm}{\textbf{logo images}} & \textbf{RoIs} \bigstrut[b]\\
 %\hline
-%{total} & & {143 (union)} & {1,218} & {10,298} \bigstrut[t]\\
-\end{tabular}
-\end{small}
-\endgroup
-\end{table}
+%football-1 & \multirow{3}{*}{train} & {104} & {331} & {3,329} \bigstrut[t]\\
+%{ski} & & {27} & {179} & {701} \\
+%{ice hockey} & & {19} & {410} & {3,920} \bigstrut[b]\\
+%\hline
+%{football-2} & test & 40 & 298 & 2,348 \bigstrut\\
+%%\hline
+%%{total} & & {143 (union)} & {1,218} & {10,298} \bigstrut[t]\\
+%\end{tabular}
+%\end{small}
+%\endgroup
+%\end{table}
 %
@@
 \centering%
-\includegraphics[width=\linewidth, trim=0cm 7cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
-\caption{Detection+Classification FROC curve for SportsLogos test set. \map is given in brackets.}%
+\includegraphics[width=\linewidth, trim=0cm 8cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
+\caption{Detection+Classification FROC curve for SportsLogos test set. \map~is given in brackets.}%
 \label{fig:classificationFrocFootball}
@@
 \label{sec:conclusion}
-\noindent- significant improvement over baseline
-- enables novel applications
-- novel large scale in-the-wild logo dataset
-%TODO write text here
+\noindent The limits of closed set logo retrieval approaches motivate the proposed open set approach.
+By this, generalization to unseen logos and novel domains is improved significantly in comparison to a naive extension of closed set approaches to open set configurations.
+Due to the large logo variety, open set logo retrieval is still a challenging task where trained methods benefit significantly from larger datasets.
+The lack of sufficient data is addressed by introduction of the large-scale Logos in the Wild dataset.
+Despite being bigger than all other in-the-wild logo datasets combined, dataset sizes should probably be scaled even further in the future.
+Adding the Logos in the Wild data to train improved detection and comparison \acp{CNN} improves the mean average precision from 0.368 to 0.464 for open set logo retrieval on FlickrLogos-32.
+
+%\noindent- significant improvement over baseline
+%- enables novel applications
+%- novel large scale in-the-wild logo dataset
+%%TODO write text here
 

### 2017-09-06 paper-review.tex
alpha version of chapter 3, 4

--- 2017-09-04 paper-review.tex
@@
 %- different base networks: VGG-CNN-M, VGG16
-% TODO
 \noindent The current state-of-the-art approach for scene retrieval is to create a global feature of the input image.
@@
 
-Therefore, we choose a two-stage approach consisting of logo detection and logo classification as illustrated in figure~\ref{fig:pipeline}. First, the logos have to be detected in the input image. 
-There are a lot of options to search for objects as explained in cha.
-Girshick et al.
-\cite{ren2015} proposed the Faster R-CNN, for end to end learning to detect and classify objects on an image.
-This network has a bounding box regressor for each trained class, thus it is capable to produce object type specific region proposals.
+Therefore, we chose a two-stage approach consisting of logo detection and logo classification as illustrated in figure~\ref{fig:pipeline}. First, the logos have to be detected in the input image. 
+There are a lot of options to search for objects.
+We utilized Faster R-CNN network to detect logos in images, proposed by Girshick et al.
+\cite{ren2015}.
+It made the selection of an appropriate baseline method easier, since currently almost only Faster R-CNNs are used in the context of logo retrieval.
+Nevertheless, these solutions are not suitable to detect logos in an open-set manner, by considering only the class probability distribution.
+Therefore, the task raises the need for a generic logo detector, which is able to detect every kind of logos.
+During the training of a Faster R-CNN, a Region Proposal Network will be trained to detect all the objects, which it was trained on.
+It provides a decision whether a region of the image is a logo or not.
+The trained RPN and the underlying feature extractor network can be extracted and employed as a universal detector.
+Another option to detect logos is a class agnostic Faster R-CNN, which is trained with two classes: background and logo.
+We argue, that this solution yields better performance than the RPN detector because of two reasons.
+Firstly, because of the fully connected layers preceding the final classifier serving a strong classification power and the bounding box regression layers, making further bounding box adjustments.
+Secondly, the combination of RPN and the FC classifier shape a cascade of detectors, similarly as in \cite{viola2004}, where the RPN counts for a weaker classifier, which is faster and allowing more false positives.
+For the combination it is expected to have a lower false positive rate.
 
@@
 %TODO write text here
+After a logo is detected in an image, a correspondence from the query set should be searched.
+In order to retrieve as much objects from the images as possible, the detectors should work with a high recall.
+Although, for difficult tasks like open-set logo detection, high recall values induce usually a lot of false positive possible object locations.
+These examples should be eliminated by appropriate classifier.
+However, in case of image retrieval the goal is not direct classification, but rather feature extraction of a found region.
+Thus, the features of the logos of all the query images and the search set should be collected.
+The retrieved feature vectors are then normalized and the similarities of them are calculated with cosine similarity.
+For baseline method, a Faster R-CNN is utilized, trained as usual.
+During inference, instead of detecting and classifying directly from the class probabilities, first the logos will be detected by processing the output of the RPN.
+Then, the class scores are used as discriminative feature for the underlying region.
+The feature vector of the query images are extracted from the complete image, since the logos fill the majority of these images.
+Donahue et al.
+proposed \cite{donahue2015}, that convolutional networks can produce excellent descriptors of the input image, regardless of the absence of fine-tuning to the specific context of the image.
+For this purpose, a network is pretrained on very large datasets, after which it can be deployed for a broad set of computer vision problems.
+In our case, the networks were additionally fine-tuned with different amount of logo images.
+The proposed logo retrieval system consists of a class agnostic logo detector and a feature extractor network.
+This setup is advantageous for the quality of the extracted features, because the complete network is only focused on a specific region.
 
@@
 \hline
-\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 631 & 6,084 & 17,738 \bigstrut[t]
+\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 868 & 11,039 & 32,808 \bigstrut[t]
 \end{tabular}

### 2017-09-06 dataset_preparation/create_clean_dataset.py

@@ -345,7 +345,7 @@ if __name__ == '__main__':
                 if brand == "coke1":
                     brand = "coke"
                 if brand == "copyofamcrest-symbol":
-                    imagebrands.append('')
+                    root.remove(obj)
                     continue
                 if brand == "corona":
                     brand = "corona-text"
@@ -510,9 +510,6 @@ if __name__ == '__main__':
                 if args.wofl32 and brand in fl32_intersection:
                     intersection = True
 
-                print(roiname)
-                print(brand)
-
                 if args.roi:
                     bndbox = obj.find('bndbox')
                     x1 = int(bndbox[0].text)
@@ -536,8 +533,6 @@ if __name__ == '__main__':
                 
                 brand = imagebrands[roiCounter]
                 roiCounter += 1
-                if brand == '':
-                    continue
                 
                 bndbox = obj.find('bndbox')
                 x1 = int(bndbox[0].text)

### 2017-09-06 paper-review.tex

--- 2017-09-05 paper-review.tex
@@
 %All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
-After removing duplicates, this results in 4~to 574~images per searched brand. These images are then one-by-one manually annotated with logo bounding boxes or sorted out if unsuitable.
+After removing duplicates, this results in 4~to 608~images per searched brand. These images are then one-by-one manually annotated with logo bounding boxes or sorted out if unsuitable.
 Images are considered unsuitable if they contain no logos or fail the in-the-wild requirement, which is the case for the original raw logo graphics.

### 2017-09-06 paper-review.tex
Reworked section 3. Added open set figure.

@@
 \newacro{PCA}{Principle Component Analysis}
+\newacro{RPN}{Region Proposal Network}
 \newacro{SIFT}{Scale Invariant Feature Transform}
@@
 \begin{document}
+% overall list of remaining stuff
+%TODO figures: commas => dots
+%TODO anonymize review version
+%TODO denote dataset as work in progress and training version as 'v1.0'
 
@@
 Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption.
-To address this issue, an open set logo retrieval method is proposed in this work which allows search for previously unfamiliar logos only by one query sample.
+To address this issue, an open set logo retrieval method is proposed in this work which allows searching for previously unfamiliar logos only by one query sample.
 A two stage concept with an open set logo detection and comparison is proposed.
@@
 The YOLO detector \cite{redmon2015} introduces an end-to-end network for object detection and classification based on bounding box regressors for object localization.
-This concept is similarly applied by the Single Shot MultiBox Detector (SSD) \cite{liu2015}.
-Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a region proposal network (RPN) to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network.
+This concept is similarly applied by the Single Shot MultiBox Detector (SSD) \cite{liu2016b}.
+Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a \ac{RPN} to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network.
 Improvements of the Faster R-CNN are the Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b}, which reduces inference time by an end-to-end fully convolutional network, and the Mask R-CNN \cite{he2017}, adding a classification mask for instance segmentation.
@@
 \centering%
-\includegraphics[width=\linewidth, trim=0cm 5cm 0cm 0cm, clip]{img/openset.pdf}%
+\includegraphics[width=\linewidth, trim=0cm 6.6cm 0cm 0cm, clip]{img/openset.pdf}%
 \caption{Comparison of closed and open set logo retrieval strategy.}%
@@
 %- different base networks: VGG-CNN-M, VGG16
-\noindent The current state-of-the-art approach for scene retrieval is to create a global feature of the input image.
-This is achieved either by inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature.
+\noindent The current state-of-the-art approaches for scene retrieval create a global feature of the input image.
+This is achieved by either inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature \cite{torii2015,arandjelovic2016,kalantidis2016}.
 For logo retrieval, extraction of a global feature is counterproductive because it lacks discriminative power to retrieve small objects.
-Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval.
+Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval applications.
 
-Therefore, we chose a two-stage approach consisting of logo detection and logo classification as illustrated in figure~\ref{fig:pipeline}. First, the logos have to be detected in the input image. 
-There are a lot of options to search for objects.
-We utilized Faster R-CNN network to detect logos in images, proposed by Girshick et al.
-\cite{ren2015}.
-It made the selection of an appropriate baseline method easier, since currently almost only Faster R-CNNs are used in the context of logo retrieval.
-Nevertheless, these solutions are not suitable to detect logos in an open-set manner, by considering only the class probability distribution.
-Therefore, the task raises the need for a generic logo detector, which is able to detect every kind of logos.
-During the training of a Faster R-CNN, a Region Proposal Network will be trained to detect all the objects, which it was trained on.
-It provides a decision whether a region of the image is a logo or not.
-The trained RPN and the underlying feature extractor network can be extracted and employed as a universal detector.
-Another option to detect logos is a class agnostic Faster R-CNN, which is trained with two classes: background and logo.
-We argue, that this solution yields better performance than the RPN detector because of two reasons.
-Firstly, because of the fully connected layers preceding the final classifier serving a strong classification power and the bounding box regression layers, making further bounding box adjustments.
-Secondly, the combination of RPN and the FC classifier shape a cascade of detectors, similarly as in \cite{viola2004}, where the RPN counts for a weaker classifier, which is faster and allowing more false positives.
-For the combination it is expected to have a lower false positive rate.
+Therefore, we choose a two-stage approach consisting of logo detection and logo classification as figure~\ref{fig:openClosedSet} illustrates for the open set case.
+First, the logos have to be detected in the input image.
+Since currently almost only Faster R-CNNs~\cite{ren2015} are used in the context of logo retrieval, we follow this choice for better comparability and because it offers a straight forward baseline method.
+Other state-of-the-art detector options, such as SSD \cite{liu2016b} or YOLO \cite{redmon2016}, potentially offer a faster detection at the cost of detection performance \cite{huang2016b}.
+
+Detection networks trained for the currently common closed set assumption are unsuitable to detect logos in an open set manner.
+By considering the output brand probability distribution, no derivation about occurrences of other brands are possible.
+Therefore, the task raises the need for a generic logo detector, which is able to detect all logo brands in general.
+
+\subsubsection*{Baseline}
+\vspace*{-2.5mm}
+Faster R-CNN consists of two stages, the first being a \ac{RPN} to detect object candidates in the feature maps and the second being classifiers for the candidate regions.
+While the second stage specifies on the trained brands, the \ac{RPN} will generate candidates that vaguely resemble any of the brands which is the case for many other logos.
+Thus, it provides an indicator whether a region of the image is a logo or not.
+The trained \ac{RPN} and the underlying feature extractor network are extracted and employed as a baseline open set logo detector.
+
+\subsubsection*{Brand Agnostic}
+\vspace*{-2.5mm}
+The \ac{RPN} strategy is by no means optimal because it obviously has a bias towards the pre-trained brands and also includes a certain amount of false positives.
+Therefore, another option to detect logos is suggested which we call the brand agnostic Faster R-CNN.
+It is trained with only two classes: background and logo.
+We argue that this solution which merges all brands into a single class yields better performance than the \ac{RPN} detector because of two reasons.
+First, in the second stage fully connected layers preceding the output layer serve as strong classifiers which are able to eliminate false positives.
+Second, the bounding box regression layers better adapt the bounding boxes to the logos resulting in a more precise localization. 
+%Third, the combination of \ac{RPN} and the fully connected classifiers shape a cascade of detectors similarly as in \cite{viola2004}.
+The \ac{RPN} counts for a weaker classifier, which is faster and allows more false positives.
+In combination, it is expected to have a lower false positive rate.
 
@@
 %TODO write text here
-After a logo is detected in an image, a correspondence from the query set should be searched.
+\noindent After a logo is detected in an image, a correspondence from the query set should be searched.
 In order to retrieve as much objects from the images as possible, the detectors should work with a high recall.
@@
 For baseline method, a Faster R-CNN is utilized, trained as usual.
-During inference, instead of detecting and classifying directly from the class probabilities, first the logos will be detected by processing the output of the RPN.
+During inference, instead of detecting and classifying directly from the class probabilities, first the logos will be detected by processing the output of the \ac{RPN}.
 Then, the class scores are used as discriminative feature for the underlying region.
@@
 Even the union of all related logo datasets contains significantly less brands and RoIs which makes Logos in the Wild a valuable large-scale dataset.
- %Table~\ref{tab:datasetStatistics} gives more details.
 The annotation is still an ongoing process and further larger versions of the dataset are expected to be published in the future (??).
@@
 
-In all cases the \acp{CNN} are trained until convergence which requires ??
-to ??k iterations with a batch-size of ??.
-Training duration depends on the architecture as well as the amount of training data.
+In all cases, the \acp{CNN} are trained until convergence.
+Due to the diversity of applied networks and differing dataset sizes, training settings are numerous and optimized in each case with the validation data.
+Convergence occurs after 1,000 to 80,000 training iterations with a batch-size between 1 for the Faster R-CNN detector and 32 for the VGG16 training.
+%Training duration depends on the architecture as well as the amount of training data.
 %TODO write text here
@@
 \subsection{Detection}
-%- train 3 different detectors: multi-class Faster R-CNN (maybe RPN), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
+%- train 3 different detectors: multi-class Faster R-CNN (maybe \ac{RPN}), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
 %- test on FlickrLogos-32 => FROC plot\\
@@
 As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
-It is naively adapted to open set detection by using the RPN scores as detections.
+It is naively adapted to open set detection by using the \ac{RPN} scores as detections.
 This skips the closed set classification part of the network which is trained on different logos than should be detected on the test set.
@@
 %the RPN scores serve as detections.
-The proposed logo detector is first trained on the same public data for comparison. The results in figure~\ref{fig:detectionFroc} indicate that this strategy is superior by a significant margin. 
+The proposed logo detector is first trained on the same public data for comparison. All Faster R-CNN detectors are based on VGG16 network.
+The results in figure~\ref{fig:detectionFroc} indicate that the proposed brand agnostic strategy is superior by a significant margin. 
 %
@@
 \includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/detectionFroc.pdf}%
-\caption{Detection FROC curves for FlickrLogos-32 test set.}%
+\caption{Detection FROC curves for the FlickrLogos-32 test set.}%
 \label{fig:detectionFroc}
@@
 \centering%
-\includegraphics[width=\linewidth, trim=0cm 7cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
-\caption{Detection+Classification FROC curves for FlickrLogos-32 test set.
+\includegraphics[width=\linewidth, trim=0cm 7.4cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
+\caption{Detection+Classification FROC curves for the FlickrLogos-32 test set.
 Including dashed indicators for one standard deviation.
@@
 \centering%
-\includegraphics[width=\linewidth, trim=0cm 8cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
-\caption{Detection+Classification FROC curve for SportsLogos test set. \map~is given in brackets.}%
+\includegraphics[width=\linewidth, trim=0cm 8.5cm 0cm 0cm, clip]{img/classificationFrocFootball.pdf}%
+\caption{Detection+Classification FROC curves for the Sports\-Logos test set, \map~is given in brackets.}%
 \label{fig:classificationFrocFootball}

### 2017-09-07 paper-review.tex
small changes

@@
 We argue that this approach is also required for logo retrieval because of the vast amount of existing brands and according logos which cannot be captured in advance.
-Typically, approaches targeting open set scenarios consist of an object detector and a feature extractor~\cite{??}.
+Typically, approaches targeting open set scenarios consist of an object detector and a feature extractor~\cite{zheng2016b}.
 The detector localizes the objects of interest and the feature extractor creates a discriminative descriptor regarding the target classes which can than be compared to query samples.
@@
 Due to the diversity of applied networks and differing dataset sizes, training settings are numerous and optimized in each case with the validation data.
-Convergence occurs after 1,000 to 80,000 training iterations with a batch-size between 1 for the Faster R-CNN detector and 32 for the VGG16 training.
+Convergence occurs after 200 to 8,000 training iterations with a batch-size between 1 for the Faster R-CNN detector, 32 for the VGG16, 18 for the ResNet101 and 7 for the DenseNet161 training, due to GPU memory limitation.
 %Training duration depends on the architecture as well as the amount of training data.

### 2017-09-07 paper-review.tex
Reworked section 4. Polishing and proofreading.

@@
 % overall list of remaining stuff
-%TODO figures: commas => dots
-%TODO anonymize review version
-%TODO denote dataset as work in progress and training version as 'v1.0'
+%TODO final proofreading
 
@@
 
-\author{\authorname{Andras T\"uzk\"o\sup{1}, Christian Herrmann\sup{1,2}, Daniel Manger\sup{1}, Dieter Willersinn\sup{1}, J\"urgen Beyerer\sup{1,2}}
-\affiliation{\sup{1} Fraunhofer IOSB, Karlsruhe, Germany}
-\affiliation{\sup{2} Karlsruhe Institute of Technology KIT, Vision and Fusion Lab, Karlsruhe, Germany}
-\email{$\lbrace$andras.tuezkoe$|$christian.herrmann$|$daniel.manger$|$dieter.willersinn$\rbrace$@iosb.fraunhofer.de}
-%\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
-}
+\author{{\large Paper ID 666??}}
+%\author{\authorname{Andras T\"uzk\"o\sup{1}, Christian Herrmann\sup{1,2}, Daniel Manger\sup{1}, Dieter Willersinn\sup{1}, J\"urgen Beyerer\sup{1,2}}
+%\affiliation{\sup{1} Fraunhofer IOSB, Karlsruhe, Germany}
+%\affiliation{\sup{2} Karlsruhe Institute of Technology KIT, Vision and Fusion Lab, Karlsruhe, Germany}
+%\email{$\lbrace$andras.tuezkoe$|$christian.herrmann$|$daniel.manger$|$dieter.willersinn$\rbrace$@iosb.fraunhofer.de}
+%%\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
+%}
 
@@
 We argue that the logo domain is too large for this strategy and requires an open set approach.
-To foster research in this direction, the large-scale Logos in the Wild dataset is collected and released to the public.
-Searching for logos in image data has many applications, with judging the effectiveness of advertisement in sports event broadcasts being one example.
-Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a database of images or videos.
-Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption.
-To address this issue, an open set logo retrieval method is proposed in this work which allows searching for previously unfamiliar logos only by one query sample.
-A two stage concept with an open set logo detection and comparison is proposed.
-Both modules are based on task specific \acp{CNN}.
-The novel Logos in the Wild dataset serves to train the modules with sufficient appropriate in-the-wild data.
-The proposed method extends the application field in comparison to closed set approaches and significant improvements over baseline methods derived from these state-of-the-art closed set approaches are shown.
+To foster research in this direction, a large-scale logo dataset, called Logos in the Wild, is collected and released to the public.
+A typical open set logo retrieval applications is, for example, judging the effectiveness of advertisement in sports event broadcasts.
+Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a set of images or videos.
+Currently common logo retrieval approaches are unsuitable for this task because of their closed world assumption.
+Thus, an open set logo retrieval method is proposed in this work which allows searching for previously unfamiliar logos by a single query sample.
+A two stage concept with separate logo detection and comparison is proposed where both modules are based on task specific \acp{CNN}.
+If trained with the Logos in the Wild data, significant performance improvements are observed, especially compared with state-of-the-art closed set approaches.
+%serves to train the modules with sufficient appropriate in-the-wild data. 
+%The proposed method extends the application field in comparison to closed set approaches and significant improvements over baseline methods derived from these state-of-the-art closed set approaches are shown.
 }
@@
 In most applications this prior knowledge is given in shape of training data.
-This requirement excludes basically all current logo retrieval approaches because they make a closed-world assumption where all searched logos are known beforehand.
+This requirement excludes basically all current logo retrieval approaches because they make a closed world assumption where all searched logos are known beforehand.
 Instead, this paper focuses on open set logo retrieval where only one sample image of a logo is available.
@@
 Thus, a brand might also refer to a product or company name if an according logo exists.}.
-The METU trademark dataset~\cite{tursun2017} contains, for example, over half a million different logos.
-Given this number, a closed set approach where all different logos are pretrained within the retrieval system is clearly inappropriate.
+The METU trademark dataset~\cite{tursun2017} contains, for example, over half a million different brands.
+Given this number, a closed set approach where all different brands are pre-trained within the retrieval system is clearly inappropriate.
 This is why our proposed feature extractor generates a discriminative logo descriptor, which generalizes to unseen logos, instead of a mere classification between previously known brands.
@@
 Especially, occlusions, blur and variations within a logo type are only partially covered.
-To address these shortcomings, a novel in-the-wild logo dataset is collected and made publicly available~\footnote{\url{url://to.come}}.
+To address these shortcomings, the novel Logos in the Wild dataset is collected and made publicly available~\footnote{\url{url://to.come}}.
 
@@
 \cite{iandola2015} and achieved superior results on the FlickrLogos-32 dataset \cite{romberg2011}.
-Furthermore, R-CNN, Fast R-CNN and Faster R-CNN were used in \cite{bao2016}, \cite{oliveira2016}, \cite{qi2017}.
-All these works use the same brands for training as for validation.
+Furthermore, R-CNN, Fast R-CNN and Faster R-CNN were used in \cite{bao2016,oliveira2016,qi2017}.
+As closed set methods, all of them use the same brands for training as for validation.
 
@@
 \subsection{Open Set Retrieval}
-Retrieval scenarios in other domains are basically always considered open set, \xie samples from the currently searched class have never been seen before.
+Retrieval scenarios in other domains are basically always considered open set, \xie,~samples from the currently searched class have never been seen before.
 This is the case for general purpose image retrieval~\cite{sivic2003}, tattoo retrieval~\cite{manger2012} or for person retrieval in image or video data where face or appearance-based methods are common~\cite{bauml2010,weber2011,herrmann2015b}.
 The reason is that these in-the-wild scenarios offer usually a too large and impossible to capture variety of object classes.
-In case of persons, a class would be a person identity with billions of persons existing.
-Consequently, methods have to be designed and trained on a limited set of classes and have to generalize to previously unseen classes.
+In case of persons, a class would be a person identity resulting in a cardinality of billions.
+Consequently, methods are designed and trained on a limited set of classes and have to generalize to previously unseen classes.
 We argue that this approach is also required for logo retrieval because of the vast amount of existing brands and according logos which cannot be captured in advance.
@@
 Nowadays, deep learning methods surpass the traditional methods by a significant margin.
-In addition, they allow a certain level of object classification within the detector which is mostly used to simultaneously detect different object categories \cite{sermanet2013}.
+In addition, they allow a certain level of object classification within the detector which is mostly used to simultaneously detect different object categories, such as  persons and cars \cite{sermanet2013}.
 %The OverFeat framework uses sliding windows on multiple scales of the image and combines the \ac{CNN} features to detect objects and classify them. 
@@
 
-\section{\uppercase{Logo Detection}}
-%\noindent- class agnostic detector \\
-%- different base networks: VGG-CNN-M, VGG16
-\noindent The current state-of-the-art approaches for scene retrieval create a global feature of the input image.
-This is achieved by either inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature \cite{torii2015,arandjelovic2016,kalantidis2016}.
-For logo retrieval, extraction of a global feature is counterproductive because it lacks discriminative power to retrieve small objects.
-Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval applications.
-
-Therefore, we choose a two-stage approach consisting of logo detection and logo classification as figure~\ref{fig:openClosedSet} illustrates for the open set case.
-First, the logos have to be detected in the input image.
-Since currently almost only Faster R-CNNs~\cite{ren2015} are used in the context of logo retrieval, we follow this choice for better comparability and because it offers a straight forward baseline method.
-Other state-of-the-art detector options, such as SSD \cite{liu2016b} or YOLO \cite{redmon2016}, potentially offer a faster detection at the cost of detection performance \cite{huang2016b}.
-
-Detection networks trained for the currently common closed set assumption are unsuitable to detect logos in an open set manner.
-By considering the output brand probability distribution, no derivation about occurrences of other brands are possible.
-Therefore, the task raises the need for a generic logo detector, which is able to detect all logo brands in general.
-
-\subsubsection*{Baseline}
-\vspace*{-2.5mm}
-Faster R-CNN consists of two stages, the first being a \ac{RPN} to detect object candidates in the feature maps and the second being classifiers for the candidate regions.
-While the second stage specifies on the trained brands, the \ac{RPN} will generate candidates that vaguely resemble any of the brands which is the case for many other logos.
-Thus, it provides an indicator whether a region of the image is a logo or not.
-The trained \ac{RPN} and the underlying feature extractor network are extracted and employed as a baseline open set logo detector.
-
-\subsubsection*{Brand Agnostic}
-\vspace*{-2.5mm}
-The \ac{RPN} strategy is by no means optimal because it obviously has a bias towards the pre-trained brands and also includes a certain amount of false positives.
-Therefore, another option to detect logos is suggested which we call the brand agnostic Faster R-CNN.
-It is trained with only two classes: background and logo.
-We argue that this solution which merges all brands into a single class yields better performance than the \ac{RPN} detector because of two reasons.
-First, in the second stage fully connected layers preceding the output layer serve as strong classifiers which are able to eliminate false positives.
-Second, the bounding box regression layers better adapt the bounding boxes to the logos resulting in a more precise localization. 
-%Third, the combination of \ac{RPN} and the fully connected classifiers shape a cascade of detectors similarly as in \cite{viola2004}.
-The \ac{RPN} counts for a weaker classifier, which is faster and allows more false positives.
-In combination, it is expected to have a lower false positive rate.
-
-% Logo comparison and classification can be included in the Faster R-CNN framework at the cost of generalization to unseen classes.
-We argue that specialization to a few dozen specific brands does not cover the complexity and breadth of the domain.
-
-\section{\uppercase{Logo Comparison}}
-%TODO write text here
-\noindent After a logo is detected in an image, a correspondence from the query set should be searched.
-In order to retrieve as much objects from the images as possible, the detectors should work with a high recall.
-Although, for difficult tasks like open-set logo detection, high recall values induce usually a lot of false positive possible object locations.
-These examples should be eliminated by appropriate classifier.
-However, in case of image retrieval the goal is not direct classification, but rather feature extraction of a found region.
-Thus, the features of the logos of all the query images and the search set should be collected.
-The retrieved feature vectors are then normalized and the similarities of them are calculated with cosine similarity.
-For baseline method, a Faster R-CNN is utilized, trained as usual.
-During inference, instead of detecting and classifying directly from the class probabilities, first the logos will be detected by processing the output of the \ac{RPN}.
-Then, the class scores are used as discriminative feature for the underlying region.
-The feature vector of the query images are extracted from the complete image, since the logos fill the majority of these images.
-Donahue et al.
-proposed \cite{donahue2015}, that convolutional networks can produce excellent descriptors of the input image, regardless of the absence of fine-tuning to the specific context of the image.
-For this purpose, a network is pretrained on very large datasets, after which it can be deployed for a broad set of computer vision problems.
-In our case, the networks were additionally fine-tuned with different amount of logo images.
-The proposed logo retrieval system consists of a class agnostic logo detector and a feature extractor network.
-This setup is advantageous for the quality of the extracted features, because the complete network is only focused on a specific region.
-
-\section{\uppercase{Logo Dataset}}
-%\noindent- freely collected from web \\
-%- name suggestions: 'Logos in the Wild', 'IOSB Logos' \\
-%- how was the dataset collected? \\
-%- database statistics \\
-%- what is different compared with other datasets? \\
-%- what are the benefits? \\
-%%TODO Christian
-\noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets.
-A comparison to other public in-the-wild datasets with annotated bounding boxes is given in table~\ref{tab:logoDatasets}.
-%
 \begin{table*}[t]
 \centering
-\caption{Publicly available in-the-wild logo datasets in comparison with the novel dataset.}
+\caption{Publicly available in-the-wild logo datasets in comparison with the novel Logos in the Wild dataset.}
 \label{tab:logoDatasets}
@@
 %
-The goal is an in-the-wild logo dataset with pictures including logos instead of the pure original logo graphics.
-In addition, images where the logo does not represent the central dominant part of the image are preferred.
-See figure~\ref{fig:logoSamples} for a few examples of the collected data.
+\section{\uppercase{Logo Detection}}
+%\noindent- class agnostic detector \\
+%- different base networks: VGG-CNN-M, VGG16
+\noindent The current state-of-the-art approaches for scene retrieval create a global feature of the input image.
+This is achieved by either inferring from the complete image or by searching for key regions and then extracting features from the located regions, which are finally fused into a global feature \cite{torii2015,arandjelovic2016,kalantidis2016}.
+For logo retrieval, extraction of a global feature is counterproductive because it lacks discriminative power to retrieve small objects.
+Additionally, global features usually include no information about the size and location of the objects which is also an important factor for logo retrieval applications.
+
+Therefore, we choose a two-stage approach consisting of logo detection and logo classification as figure~\ref{fig:openClosedSet} illustrates for the open set case.
+First, the logos have to be detected in the input image.
+Since currently almost only Faster R-CNNs~\cite{ren2015} are used in the context of logo retrieval, we follow this choice for better comparability and because it offers a straight forward baseline method.
+Other state-of-the-art detector options, such as SSD \cite{liu2016b} or YOLO \cite{redmon2016}, potentially offer a faster detection at the cost of detection performance \cite{huang2016b}.
+
+Detection networks trained for the currently common closed set assumption are unsuitable to detect logos in an open set manner.
+By considering the output brand probability distribution, no derivation about occurrences of other brands are possible.
+Therefore, the task raises the need for a generic logo detector, which is able to detect all logo brands in general.
+
+\subsubsection*{Baseline}
+\vspace*{-2.5mm}
+Faster R-CNN consists of two stages, the first being an \ac{RPN} to detect object candidates in the feature maps and the second being classifiers for the candidate regions.
+While the second stage sharply classifies the trained brands, the \ac{RPN} will generate candidates that vaguely resemble any of the brands which is the case for many other logos.
+Thus, it provides an indicator whether a region of the image is a logo or not.
+The trained \ac{RPN} and the underlying feature extractor network are isolated and employed as a baseline open set logo detector.
+
+\subsubsection*{Brand Agnostic}
+\vspace*{-2.5mm}
+The \ac{RPN} strategy is by no means optimal because it obviously has a bias towards the pre-trained brands and also generates a certain amount of false positives.
+Therefore, another option to detect logos is suggested which we call the brand agnostic Faster R-CNN.
+It is trained with only two classes: background and logo.
+We argue that this solution which merges all brands into a single class yields better performance than the \ac{RPN} detector because of two reasons.
+First, in the second stage, fully connected layers preceding the output layer serve as strong classifiers which are able to eliminate false positives.
+Second, these layers also serve as stronger bounding box regressors improving the localization precision of the logos.
+
+\section{\uppercase{Logo Comparison}}
+\noindent After logos are detected, the correspondences to the query sample have to be searched. 
+For logo retrieval, features are extracted from the detected logos for comparison with the query sample.
+Thus, the logo feature vectors for the query image and the ones for the database are collected and normalized.
+Pair-wise comparison is then performed by cosine similarity.
+
+In order to retrieve as many logos from the images as possible, the detector has to operate at a high recall.
+However, for difficult tasks, such as open set logo detection, high recall values induce a certain amount of false positive detections.
+The feature extraction step thus has to be robust and tolerant to these false positives.
+%These have to be eliminated by an appropriate subsequent classifier. 
+%
+%As baseline feature extraction method, a standard Faster R-CNN is utilized, trained  with the training set classes. 
+%During inference, instead of detecting and classifying directly from the class probabilities, first the logos will be detected by processing the output of the \ac{RPN}.
+Then, the class scores are used as discriminative feature for the underlying region.
+%
+%The feature vector of the query images are extracted from the full query image since they are assumed to be either manually picked, or previously detected and cropped by a logo detector.
+%
+
+Donahue et al. suggested that \acp{CNN} can produce excellent descriptors of an input image  even in the absence of fine-tuning to the specific domain of the image \cite{donahue2015}. 
+This motivates to apply a network pre-trained on a very large dataset as feature extractor.
+Namely, several state-of-the-art \acp{CNN} trained on the ImageNet dataset \cite{deng2009} are explored for this task.
+To adjust the network to the logo domain and the false positive removal, the networks are fine-tuned on logo detections.
+The final network layer is extracted as logo feature in all cases.
+
+Altogether, the proposed logo retrieval system consists of a class agnostic logo detector and a feature extractor network.
+This setup is advantageous for the quality of the extracted logo features because the extractor network has only to focus on a specific region.
+This is an improvement compared to including both logo detection and comparison in the regular Faster R-CNN framework which lacks generalization to unseen classes.
+We argue that the specialization in the regular Faster R-CNN to the limited number of specific brands in the training set does not cover the complexity and breadth of the logo domain.
+This is why a separate and more elaborate feature extractor is proposed even though this might appear like a less elegant solution.
+
 %
@@
 %
+\section{\uppercase{Logo Dataset}}
+%
+\begin{figure}%
+\centering%
+\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
+\caption{Annotations differentiate between textual and graphical logos.}%
+\label{fig:annotatedSample}
+\end{figure}%
+%
+\noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets.
+A comparison to other public in-the-wild datasets with annotated bounding boxes is given in table~\ref{tab:logoDatasets}.
+The goal is an in-the-wild logo dataset with images including logos instead of the raw original logo graphics.
+In addition, images where the logo represents only a minor part of the image are preferred.
+See figure~\ref{fig:logoSamples} for a few examples of the collected data.
 Following the general suggestions from \cite{bansal2017}, we target for a dataset containing significantly more brands instead of collecting additional image samples for the already covered brands.
@@
 Annotations distinguish between textual and graphical logos as well as different logos from one company as exemplary indicated in figure~\ref{fig:annotatedSample}.
-%
-\begin{figure}%
-\centering%
-\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
-\caption{Annotations differentiate between textual and graphical logos.}%
-\label{fig:annotatedSample}
-\end{figure}%
-%
-Altogether, the current version of the dataset, which is used in this paper, contains 872 brands with 32,850 annotated bounding boxes.
+Altogether, the current version of the dataset, contains 872 brands with 32,850 annotated bounding boxes.
 238 brands occur at least 10 times.
 An image may contain several logos with the maximum being 118 logos in one image.
-The complete distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}.
+The full distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}.
+
+The collected Logos in the Wild dataset exceeds the size of all related logo datasets as shown in table~\ref{tab:logoDatasets}.
+Even the union of all related logo datasets contains significantly less brands and RoIs which makes Logos in the Wild a valuable large-scale dataset.
+As the annotation is still an ongoing process, different dataset revisions will be tagged by version numbers for future reference.
+Note that the numbers in table~\ref{tab:logoDatasets} are the current state (v2.0) whereas detector and feature extractor training used a slightly earlier version with numbers given in table~\ref{tab:trainTestStatistics} (v1.0) because of the required time for training and evaluation.
 %
@@
 \end{figure}%
-
-The collected Logos in the Wild dataset exceeds the size of all related logo datasets as shown in table~\ref{tab:logoDatasets}.
-Even the union of all related logo datasets contains significantly less brands and RoIs which makes Logos in the Wild a valuable large-scale dataset.
-The annotation is still an ongoing process and further larger versions of the dataset are expected to be published in the future (??).
 %
@@
 \hline
-\multirow{2}[2]{*}{train} & public & 47    & 3.113 \bigstrut[t]\\
-      & public+\ac{LitW} & 632   & 18.960 \bigstrut[b]\\
+\multirow{2}[2]{*}{train} & public & 47    & 3,113 \bigstrut[t]\\
+      & public+\ac{LitW} v1.0 & 632   & 18,960 \bigstrut[b]\\
 \hline
-test  & FlickrLogos-32 test & 32    & 1.602 \bigstrut[t]\\
+test  & FlickrLogos-32 test & 32    & 1,602 \bigstrut[t]\\
 \end{tabular}%
@@
 Due to the diversity of applied networks and differing dataset sizes, training settings are numerous and optimized in each case with the validation data.
-Convergence occurs after 200 to 8,000 training iterations with a batch-size between 1 for the Faster R-CNN detector, 32 for the VGG16, 18 for the ResNet101 and 7 for the DenseNet161 training, due to GPU memory limitation.
-%Training duration depends on the architecture as well as the amount of training data.
-%TODO write text here
+Convergence occurs after 200 to 8,000 training iterations with a varying batch-size of 1 for the Faster R-CNN detector, 7 for the DenseNet161, 18 for the ResNet101 and 32 for the VGG16 training due to GPU memory limitation.
 
 \subsection{Detection}
-%- train 3 different detectors: multi-class Faster R-CNN (maybe \ac{RPN}), single-class Faster R-CNN, single-class Faster R-CNN + own logos\\
-%- test on FlickrLogos-32 => FROC plot\\
-%- test first two detectors on own logo dataset => FROC plot\\
-%- Example Detections\\
-%%TODO write text here
 As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
@@
 This skips the closed set classification part of the network which is trained on different logos than should be detected on the test set.
-%Because of the closed set training strategy, only brands occurring in the training set are the final outcome of this detector. 
-%Adaptation to open set detection of previously unseen logos is achieved by using the RPN scores before classification as detections.
-%Because of the strict separation of train and test brands, and the closed set training strategy
-%the RPN scores serve as detections.
-The proposed logo detector is first trained on the same public data for comparison. All Faster R-CNN detectors are based on VGG16 network.
+The proposed brand agnostic logo detector is first trained on the same public data for comparison. All Faster R-CNN detectors are based on the VGG16 network.
 The results in figure~\ref{fig:detectionFroc} indicate that the proposed brand agnostic strategy is superior by a significant margin. 
@@
 
-Further improvement is achieved by combining the public training data with the novel data.
+Further improvement is achieved by combining the public training data with the novel logo data.
 Adding \ac{LitW} as additional training data improves the detection results with its large variety of additional training brands. 
@@
 \subsection{Retrieval}
-%- train 4 to 6 additional networks: feature extraction network for public and public+own training data --- use VGG16, ResNet50, DenseNet as base network (either for both training sets or only for the public+own)
-%- describe repeated query logo strategy => 10 sample => mean + std
-%- results on FlickrLogos-32 => FROC plot\\
-%- results on own sports data => FROC plot\\
-%%TODO write text here
-%
-For the retrieval experiments, the Faster R-CNN based state-of-the-art closed set logo retrieval method from the previous section is again used as baseline.
-Now the full network is applied and the logo class probabilities are interpreted as feature vector which is then used to match previously unseen logos.
+For the retrieval experiments, the Faster R-CNN based state-of-the-art closed set logo retrieval method from the previous section serves again as baseline.
+Now the full network is applied and the logo class probabilities of the second stage are interpreted as feature vector which is then used to match previously unseen logos.
 For the proposed open set strategy, the best logo detection network from the previous section is used in all cases.
-Detected logos are described by the classification network's output feature.
-Descriptor matching is performed in all cases with cosine similarity.
-Three different state-of-the-art classification architectures, namely VGG16~\cite{simonyan2014}, ResNet101~\cite{he2015} and DenseNet161~\cite{huang2016}, serve as base for the logo classification stage.
+Detected logos are described by the feature extraction network outputs where three different state-of-the-art classification architectures, namely VGG16~\cite{simonyan2014}, ResNet101~\cite{he2015} and DenseNet161~\cite{huang2016}, serve as base networks.
 All networks are pretrained on ImageNet and afterwards fine-tuned either on the public logo train set or the combination of the public and the \ac{LitW} train data.
 
+%
+\begin{figure}%
+\centering%
+\includegraphics[width=\linewidth, trim=0cm 7.4cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
+\caption{Detection+Classification FROC curves for the FlickrLogos-32 test set.
+Including dashed indicators for one standard deviation.
+DenseNet results are omitted for clarity, refer to table~\ref{tab:mapFlickr} for full results.}%
+\label{fig:classificationFroc}
+\end{figure}%
+%
 \subsubsection*{FlickrLogos-32}
@@
 Specifically, the larger training dataset has a larger impact on the performance than a better network architecture.
-%
-\begin{figure}%
-\centering%
-\includegraphics[width=\linewidth, trim=0cm 7.4cm 0cm 0cm, clip]{img/classificationFroc.pdf}%
-\caption{Detection+Classification FROC curves for the FlickrLogos-32 test set.
-Including dashed indicators for one standard deviation.
-DenseNet results are omitted for clarity, refer to table~\ref{tab:mapFlickr} for full results.}%
-\label{fig:classificationFroc}
-\end{figure}%
-%
-%As far as we are aware, this is the first experiment with open set logo retrieval on 
 Table~\ref{tab:mapFlickr} compares our open set results with closed set results from the literature in terms of the mean average precision (\map). 
@@
 In addition, our approach is not limited to the 32 FlickrLogos brands but generalizes with a similar performance to further brands.
-In contrast, the closed-set approaches hardly generalize as is shown by the baseline open set method.
+In contrast, the closed set approaches hardly generalize as is shown by the baseline open set method.
 This is the second best closed set approach only retrained on out-of-test brands.
@@
 In total, this SportsLogos test set includes 298 annotated frames with 2,348 logos of 40 brands.
-In comparison to public logo datasets, the logos are usually significantly smaller in these cases and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}.
+In comparison to public logo datasets, the logos are usually significantly smaller and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}.
 Besides perimeter advertising, logos on clothing or equipment of the athletes and TV station or program overlays are the most occurring logo types.
@@
 \end{figure*}%
-%
-%Due to copyright reasons this internal dataset cannot be made publicly available.
-%
-%\begin{table}[t]
-%\centering
-%\begingroup	
-%\setlength{\tabcolsep}{5pt}
-%\caption{SportsLogos dataset statistics.}
-%\label{tab:sportDataStatistics}
-%\begin{small}
-%\begin{tabular}{l|cccc}
-% & \textbf{phase} & \textbf{brands} & \sizebox{1.0cm}{\textbf{logo images}} & \textbf{RoIs} \bigstrut[b]\\
-%\hline
-%football-1 & \multirow{3}{*}{train} & {104} & {331} & {3,329} \bigstrut[t]\\
-%{ski} & & {27} & {179} & {701} \\
-%{ice hockey} & & {19} & {410} & {3,920} \bigstrut[b]\\
-%\hline
-%{football-2} & test & 40 & 298 & 2,348 \bigstrut\\
-%%\hline
-%%{total} & & {143 (union)} & {1,218} & {10,298} \bigstrut[t]\\
-%\end{tabular}
-%\end{small}
-%\endgroup
-%\end{table}
+
+\section{\uppercase{Conclusions}}
+\label{sec:conclusion}
+\noindent The limits of closed set logo retrieval approaches motivate the proposed open set approach.
+By this, generalization to unseen logos and novel domains is improved significantly in comparison to a naive extension of closed set approaches to open set configurations.
+Due to the large logo variety, open set logo retrieval is still a challenging task where trained methods benefit significantly from larger datasets.
+The lack of sufficient data is addressed by introduction of the large-scale Logos in the Wild dataset.
+Despite being bigger than all other in-the-wild logo datasets combined, dataset sizes should probably be scaled even further in the future.
+Adding the Logos in the Wild data in the training improves the mean average precision from 0.368 to 0.464 for open set logo retrieval on FlickrLogos-32.
 %
@@
 %
-
-\section{\uppercase{Conclusions}}
-\label{sec:conclusion}
-\noindent The limits of closed set logo retrieval approaches motivate the proposed open set approach.
-By this, generalization to unseen logos and novel domains is improved significantly in comparison to a naive extension of closed set approaches to open set configurations.
-Due to the large logo variety, open set logo retrieval is still a challenging task where trained methods benefit significantly from larger datasets.
-The lack of sufficient data is addressed by introduction of the large-scale Logos in the Wild dataset.
-Despite being bigger than all other in-the-wild logo datasets combined, dataset sizes should probably be scaled even further in the future.
-Adding the Logos in the Wild data to train improved detection and comparison \acp{CNN} improves the mean average precision from 0.368 to 0.464 for open set logo retrieval on FlickrLogos-32.
-
-%\noindent- significant improvement over baseline
-%- enables novel applications
-%- novel large scale in-the-wild logo dataset
-%%TODO write text here
 

### 2017-09-07 paper-review.tex
some corrections

@@
 To foster research in this direction, a large-scale logo dataset, called Logos in the Wild, is collected and released to the public.
-A typical open set logo retrieval applications is, for example, judging the effectiveness of advertisement in sports event broadcasts.
+A typical open set logo retrieval application is, for example, judging the effectiveness of advertisement in sports event broadcasts.
 Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a set of images or videos.
-Currently common logo retrieval approaches are unsuitable for this task because of their closed world assumption.
+Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption.
 Thus, an open set logo retrieval method is proposed in this work which allows searching for previously unfamiliar logos by a single query sample.
@@
 A key application is the effectiveness measurement of advertisements.
-Being able to find all logos that match a query, for example, a logo of a specific company, in images allows to assess the visual frequency and prominence of logos in TV broadcasts.
+Being able to find all logos in images, that match a query, for example a logo of a specific company, allows to assess the visual frequency and prominence of logos in TV broadcasts.
 Typically, these broadcasts are sports events where sponsorship and advertisement is very common.
-This requires a flexible system where the query can easily be defined and switched according to the current task.
-Especially, also previously unseen logos should be found if one query sample is available.
+This requires a flexible system where the query can be easily defined and switched according to the current task.
+Especially, also previously unseen logos should be found even if only one query sample is available.
 %In general, open set retrieval is understood as finding instances of the same class in a database given a single instance from this class which has never been seen before.
@@
 %\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 868 & 11,039 & 32,808 \bigstrut[t]
-\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 872 & 11,054 & 32,850 \bigstrut[t]
+\begin{minipage}[c]{0.1cm}\vertboxt{new}\end{minipage} & Logos in the Wild & 871 & 11,054 & 32,850 \bigstrut[t]
 \end{tabular}
@@
 Annotations distinguish between textual and graphical logos as well as different logos from one company as exemplary indicated in figure~\ref{fig:annotatedSample}.
-Altogether, the current version of the dataset, contains 872 brands with 32,850 annotated bounding boxes.
+Altogether, the current version of the dataset, contains 871 brands with 32,850 annotated bounding boxes.
 238 brands occur at least 10 times.

### 2017-09-11 paper-final.tex
Final fixes and polishing for submission.

--- 2017-09-07 paper-review.tex
@@
 
-\author{{\large Paper ID 666??}}
+\author{\authorname{Andras T\"uzk\"o\sup{1}, Christian Herrmann\sup{1,2}, Daniel Manger\sup{1}, J\"urgen Beyerer\sup{1,2}}
+\affiliation{\sup{1} Fraunhofer IOSB, Karlsruhe, Germany}
+\affiliation{\sup{2} Karlsruhe Institute of Technology KIT, Vision and Fusion Lab, Karlsruhe, Germany}
+\email{$\lbrace$andras.tuezkoe$|$christian.herrmann$|$daniel.manger$|$juergen.beyerer$\rbrace$@iosb.fraunhofer.de}
+%\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
+}
 %\author{\authorname{Andras T\"uzk\"o\sup{1}, Christian Herrmann\sup{1,2}, Daniel Manger\sup{1}, Dieter Willersinn\sup{1}, J\"urgen Beyerer\sup{1,2}}
@@
 To foster research in this direction, a large-scale logo dataset, called Logos in the Wild, is collected and released to the public.
-A typical open set logo retrieval application is, for example, judging the effectiveness of advertisement in sports event broadcasts.
+A typical open set logo retrieval application is, for example, assessing the effectiveness of advertisement in sports event broadcasts.
 Given a query sample in shape of a logo image, the task is to find all further occurrences of this logo in a set of images or videos.
 Currently, common logo retrieval approaches are unsuitable for this task because of their closed world assumption.
-Thus, an open set logo retrieval method is proposed in this work which allows searching for previously unfamiliar logos by a single query sample.
+Thus, an open set logo retrieval method is proposed in this work which allows searching for previously unseen logos by a single query sample.
 A two stage concept with separate logo detection and comparison is proposed where both modules are based on task specific \acp{CNN}.
@@
 A key application is the effectiveness measurement of advertisements.
-Being able to find all logos in images, that match a query, for example a logo of a specific company, allows to assess the visual frequency and prominence of logos in TV broadcasts.
+Being able to find all logos in images that match a query, for example, a logo of a specific company, allows to assess the visual frequency and prominence of logos in TV broadcasts.
 Typically, these broadcasts are sports events where sponsorship and advertisement is very common.
@@
 In most applications this prior knowledge is given in shape of training data.
-This requirement excludes basically all current logo retrieval approaches because they make a closed world assumption where all searched logos are known beforehand.
+This requirement excludes basically all current logo retrieval approaches because they make a closed world assumption in which all searched logos are known beforehand.
 Instead, this paper focuses on open set logo retrieval where only one sample image of a logo is available.
@@
   \centering
-  \includegraphics[width=\linewidth]{img/outline.png}
+  \includegraphics[width=\linewidth, trim=0cm 25.4cm 0cm 0cm, clip]{img/outline.pdf}
   \caption{Proposed logo retrieval strategy.}
@@
 \end{figure}
+%%
+%\begin{figure}[t]
+%  %\vspace{-0.2cm}
+%  \centering
+%  \includegraphics[width=\linewidth]{img/outline.png}
+%  \caption{Proposed logo retrieval strategy.}
+%  \label{fig:pipeline}
+%\end{figure}
 
-The necessity for open set logo retrieval becomes obvious when having a look at the diversity and amount of existing logos and brands\footnote{The term brand is used in this work as synonym for a single logo class.
+The necessity for open set logo retrieval becomes obvious when considering the diversity and amount of existing logos and brands\footnote{The term \textit{brand} is used in this work as synonym for a single logo class.
 Thus, a brand might also refer to a product or company name if an according logo exists.}.
@@
 One challenge for training a general purpose logo detector lies in appropriate training data.
-Many logo or trademark dataset~\cite{eakins1998,hoi2015,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application.
-The need for annotated logo bounding boxes in the images limits the number of suitable datasets.
+Many logo or trademark datasets~\cite{eakins1998,hoi2015,tursun2017} only contain the original logo graphic but no in-the-wild occurrences of these logos which are required for the target application.
+The need for annotated logo bounding boxes in the images limits the number of suitable available datasets.
 Existing logo datasets~\cite{joly2009,kalantidis2011,romberg2011,letessier2012,bianco2015,su2016,bianco2017} with available bounding boxes are often restricted to a very small number of brands and mostly high quality images.
 Especially, occlusions, blur and variations within a logo type are only partially covered.
-To address these shortcomings, the novel Logos in the Wild dataset is collected and made publicly available~\footnote{\url{url://to.come}}.
+To address these shortcomings, we collect the novel Logos in the Wild dataset and make it publicly available~\footnote{\url{url://to.come}}.
 
@@
 Furthermore, R-CNN, Fast R-CNN and Faster R-CNN were used in \cite{bao2016,oliveira2016,qi2017}.
-As closed set methods, all of them use the same brands for training as for validation.
+As closed set methods, all of them use the same brands both for training and for validation.
 
@@
 This concept is similarly applied by the Single Shot MultiBox Detector (SSD) \cite{liu2016b}.
-Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a \ac{RPN} to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network.
+The work on Faster Region-Based Convolutional Neural Network (R-CNN) \cite{ren2015} introduces a \ac{RPN} to detect object candidates in the feature maps and classifies the candidate regions by a fully connected network.
 Improvements of the Faster R-CNN are the Region-based Fully Convolutional Network (R-FCN) \cite{jifengdai2016b}, which reduces inference time by an end-to-end fully convolutional network, and the Mask R-CNN \cite{he2017}, adding a classification mask for instance segmentation.
@@
 \section{\uppercase{Logo Detection}}
+\label{sec:detection}
 %\noindent- class agnostic detector \\
@@
 First, the logos have to be detected in the input image.
-Since currently almost only Faster R-CNNs~\cite{ren2015} are used in the context of logo retrieval, we follow this choice for better comparability and because it offers a straight forward baseline method.
+Since currently almost only Faster R-CNNs~\cite{ren2015} are used in the context of logo retrieval, we follow this choice for better comparability and because it offers a straightforward baseline method.
 Other state-of-the-art detector options, such as SSD \cite{liu2016b} or YOLO \cite{redmon2016}, potentially offer a faster detection at the cost of detection performance \cite{huang2016b}.
@@
 For logo retrieval, features are extracted from the detected logos for comparison with the query sample.
-Thus, the logo feature vectors for the query image and the ones for the database are collected and normalized.
+Then, the logo feature vector for the query image and the ones for the database are collected and normalized.
 Pair-wise comparison is then performed by cosine similarity.
@@
 We argue that the specialization in the regular Faster R-CNN to the limited number of specific brands in the training set does not cover the complexity and breadth of the logo domain.
-This is why a separate and more elaborate feature extractor is proposed even though this might appear like a less elegant solution.
+This is why a separate and more elaborate feature extractor is proposed.
+% even though this might appear like a less elegant solution.
 
@@
 \section{\uppercase{Logo Dataset}}
-%
-\begin{figure}%
-\centering%
-\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
-\caption{Annotations differentiate between textual and graphical logos.}%
-\label{fig:annotatedSample}
-\end{figure}%
-%
 \noindent To train the proposed logo detector and feature extractor, a novel logo dataset is collected to supplement publicly available logo datasets.
@@
 Brand or company names are searched directly or in combination with a predefined set of search terms, \xeg, `advertisement', `building', `poster' or `store'.
+%
+\begin{figure}%
+\centering%
+\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
+\caption{Annotations differentiate between textual and graphical logos.}%
+\label{fig:annotatedSample}
+\end{figure}%
+%
 
-For each search result, the first $N$ images are downloaded, where $N$ is determined by a quick manual inspection to avoid collecting too much garbage. 
+For each search result, the first $N$ images are downloaded, where $N$ is determined by a quick manual inspection to avoid collecting too many irrelevant images. 
 %All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
@@
 For a proper separation of train and test data, all brands which are present in the FlickrLogos-32 test set are removed from the public and \ac{LitW} data.
-10 percent of the remaining images are set aside for network validation in each case.
+Ten percent of the remaining images are set aside for network validation in each case.
 This results in the final training and test set sizes listed in table~\ref{tab:trainTestStatistics}.
@@
 \subsection{Detection}
-As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
-It is naively adapted to open set detection by using the \ac{RPN} scores as detections.
-This skips the closed set classification part of the network which is trained on different logos than should be detected on the test set.
+As indicated in section~\ref{sec:detection}, the baseline is the state-of-the-art closed set logo retrieval method from~\cite{su2016} which is trained on the public data and naively adapted to open set detection by using the \ac{RPN} scores as detections
+%As baseline, the state-of-the-art closed set logo retrieval method from~\cite{su2016} based on Faster R-CNN is employed and trained on the public portion of the training data.
+%It is naively adapted to open set detection by using the \ac{RPN} scores as detections.
+This skips the closed set classification part of the network which is trained on different logos as should be detected on the test set.
 The proposed brand agnostic logo detector is first trained on the same public data for comparison. All Faster R-CNN detectors are based on the VGG16 network.
@@
 \vspace*{-2.5mm}
-In 10 iterations, each of the 10 FlickrLogos-32 train samples for each brand serves as query sample.
+In ten iterations, each of the ten FlickrLogos-32 train samples for each brand serves as query sample.
 This allows to assess the statistical significance of results similar to a 10-fold-cross-validation strategy.
@@
 Specifically, the larger training dataset has a larger impact on the performance than a better network architecture.
+
 Table~\ref{tab:mapFlickr} compares our open set results with closed set results from the literature in terms of the mean average precision (\map). 
@@
 We achieve more than half of the closed set performance in terms of \map~with only one sample for a brand at test time instead of dozens or hundreds of brand samples at training time. 
+Having only a single sample is a significant harder retrieval task on FlickrLogos-32 than closed set retrieval because logo variations within a brand are uncovered by this single sample.
+The test set includes such logo variations to a certain extent which requires excellent generalization capabilities if only one query sample is available.
+
 In addition, our approach is not limited to the 32 FlickrLogos brands but generalizes with a similar performance to further brands.
-In contrast, the closed set approaches hardly generalize as is shown by the baseline open set method.
-This is the second best closed set approach only retrained on out-of-test brands.
+In contrast, the closed set approaches hardly generalize as is shown by the baseline open set method which is based on the second best closed set approach.
+The only difference is the training on out-of-test brands for the open set task.
 
@@
 In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events.
-In total, this SportsLogos test set includes 298 annotated frames with 2,348 logos of 40 brands.
+In total, this non-public test set includes 298 annotated frames with 2,348 logos of 40 brands.
 In comparison to public logo datasets, the logos are usually significantly smaller and cover only a tiny fraction of the image area as illustrated in figure~\ref{fig:footballSample}.
@@
 \centering%
-\includegraphics[width=\linewidth]{img/football-1908719_1920_cut.jpg}%
+\includegraphics[width=\linewidth, trim=0cm 0cm 0cm 0.5cm, clip]{img/football-1908719_1920_cut.jpg}%
 \caption{Example football scene with small logos in the perimeter advertising.}%
@@
 \label{sec:conclusion}
-\noindent The limits of closed set logo retrieval approaches motivate the proposed open set approach.
-By this, generalization to unseen logos and novel domains is improved significantly in comparison to a naive extension of closed set approaches to open set configurations.
-Due to the large logo variety, open set logo retrieval is still a challenging task where trained methods benefit significantly from larger datasets.
-The lack of sufficient data is addressed by introduction of the large-scale Logos in the Wild dataset.
-Despite being bigger than all other in-the-wild logo datasets combined, dataset sizes should probably be scaled even further in the future.
-Adding the Logos in the Wild data in the training improves the mean average precision from 0.368 to 0.464 for open set logo retrieval on FlickrLogos-32.
 %
@@
 %
+\noindent The limits of closed set logo retrieval approaches motivate the proposed open set approach.
+By this, generalization to unseen logos and novel domains is improved significantly in comparison to a naive extension of closed set approaches to open set configurations.
+Due to the large logo variety, open set logo retrieval is still a challenging task where trained methods benefit significantly from larger datasets.
+The lack of sufficient data is addressed by introduction of the large-scale Logos in the Wild dataset.
+Despite being bigger than all other in-the-wild logo datasets combined, dataset sizes should probably be scaled even further in the future.
+Adding the Logos in the Wild data in the training improves the mean average precision from 0.368 to 0.464 for open set logo retrieval on FlickrLogos-32.
 

### 2017-10-27 paper-final.tex
Prepared camera ready version.

@@
 Especially, occlusions, blur and variations within a logo type are only partially covered.
-To address these shortcomings, we collect the novel Logos in the Wild dataset and make it publicly available~\footnote{\url{url://to.come}}.
+To address these shortcomings, we collect the novel Logos in the Wild dataset and make it publicly available~\footnote{\url{http://s.fhg.de/logos-in-the-wild}}.
 
@@
 \subsubsection*{Baseline}
-\vspace*{-2.5mm}
+%\vspace*{-2.5mm}
 Faster R-CNN consists of two stages, the first being an \ac{RPN} to detect object candidates in the feature maps and the second being classifiers for the candidate regions.
@@
 \subsubsection*{Brand Agnostic}
-\vspace*{-2.5mm}
+%\vspace*{-2.5mm}
 The \ac{RPN} strategy is by no means optimal because it obviously has a bias towards the pre-trained brands and also generates a certain amount of false positives.
@@
 \centering%
-\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
+\includegraphics[width=\linewidth, trim=0cm 9.9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
 \caption{Annotations differentiate between textual and graphical logos.}%
@@
 The union of all public logo datasets as listed in table~\ref{tab:logoDatasets} and the novel \ac{LitW} dataset.
-For a proper separation of train and test data, all brands which are present in the FlickrLogos-32 test set are removed from the public and \ac{LitW} data.
+For a proper separation of train and test data, all brands present in the FlickrLogos-32 test set are removed from the public and \ac{LitW} data.
 Ten percent of the remaining images are set aside for network validation in each case.
@@
 Detection and matching performance is measured by the \ac{FROC} curve~\cite{miller1969} which denotes the detection or detection and identification rate versus the number of false detections.
-
+%
 In all cases, the \acp{CNN} are trained until convergence.
@@
 \subsubsection*{FlickrLogos-32}
-\vspace*{-2.5mm}
+%\vspace*{-2.5mm}
 In ten iterations, each of the ten FlickrLogos-32 train samples for each brand serves as query sample.
@@
 \subsubsection*{SportsLogos}
-\vspace*{-2.5mm}
+%\vspace*{-2.5mm}
 In addition to public data, target domain specific experiments are performed on TV broadcasts of sports events.
@@
 %
-\begin{figure*}%
+\begin{figure}%
 \centering%
@@
 \label{fig:footballSample}
-\end{figure*}%
-
-\section{\uppercase{Conclusions}}
-\label{sec:conclusion}
+\end{figure}%
 %
@@
 %
+
+\section{\uppercase{Conclusions}}
+\label{sec:conclusion}
 \noindent The limits of closed set logo retrieval approaches motivate the proposed open set approach.
@@
 
-\vfill
+%\vfill
 \bibliographystyle{apalike}
